---
title: "MT Code Network Analysis 06"
author: "Markus Rottmann"
date: "2021 04 18"
output:
  html_document:
      toc: true
      toc_depth: 5
---

****

&nbsp;

#### Description

This Code is to analyze/build the network from downloaded tweets. This is done in following two steps:

  + Step 1: Analyze who Mentions Whose _Twitter Handle_ (e.g. @markus_rottmann).
  + Step 2: Transform this Information in an Adjecency Matrix.


**Input**

  + Dataframe `df_tweets_clean_de.rds` containing tweets in English, German and "undefined" language posted by all candidates in 2020.
  
  
**Output**

  + Adjecency Matrix `test_adj_matx01.txt` mapping all candidates that mentioned another candidate at least once (who-mentions-whom).
  - Vector `namestring_nwmembers00.rds` containing the screennames of all members of the network.



****

&nbsp;

```{r setup, include=FALSE}

## 0.1: clearing memory
rm(list=ls(all=T))

## 0.2 defining options
options(repos = "https://cran.rstudio.com")
options(stringsAsFactors = FALSE)
knitr::opts_chunk$set(echo = TRUE, fig.width = 7, fig.height = 5)


## 0.3 loading (and installing) packages
# defining required packages
req_packages <- c("dplyr", "knitr", "kableExtra", "rvest", "igraph",
"ggplot2", "tibble", "quanteda", "stargazer", "tidyr", "stringr", "lme4",
"rtweet", "lubridate", "MASS")

# checking, if already installed
new_packages <- req_packages[!(req_packages %in% installed.packages()[,"Package"])]

# installing (downloading) missing packages
if(length(new_packages) > 0) {
  install.packages(new_packages)
} 

# loading required packages
lapply(req_packages, library, character.only = TRUE) 

# removing auxillary variabels
rm(req_packages, new_packages) 

# frequenty needed packages: ("dplyr", "knitr", "kableExtra", "rvest", "igraph",
# "pageviews", "WikipediR", "ggplot2", "tibble", "quanteda", "stargazer", "tidyr",
# "stringr", "lme4", "rtweet", "lubridate")

```

&nbsp;

***

#### Step 1: Who Mentions Whose _Twitter Handle_.


```{r 01 twitter_handle_mentions, include = TRUE, results = TRUE, eval = TRUE, message = FALSE, warning = FALSE}


## loading data
data00 <- readRDS(file = "./DataFrames/df_tweets_clean_de.rds") # reading-in scraped tweets


## distilling mentions
# creating a vector with screennames
vct_screennames <- unique(data00$screen_name)

# creating network list (first column = twitterer, second column = mentioned)
df_netwrk <- data00 %>%
  ungroup(.) %>% 
  unnest(., cols = c(mentions_screen_name)) %>%
  dplyr::select(., screen_name, mentions_screen_name) %>%
  filter(mentions_screen_name != "",
         mentions_screen_name %in% vct_screennames,
         mentions_screen_name != screen_name)


## deleting help-dataframe
rm(data00, vct_screennames)

```

&nbsp;

***

#### Step 2: Transformation into an Adjecency Matrix


```{r 02 transformation_adjecency_matrix, include = TRUE, results = TRUE, eval = TRUE, message = FALSE, warning = FALSE}

## creating the graph
# creating the basic graph
grph00 <- graph_from_data_frame(df_netwrk, directed = FALSE)

# creating edges (~links) and vertices (~nodes)
edgs00 <- igraph::as_data_frame(grph00, what = "edges") # creating edges (df that lists all twitterer ("from") and mentioned ("to"))
vert00 <- igraph::as_data_frame(grph00, what = "vertices") # creating vertices (1 column-df of all involved)

# filtering "from" and "to" down to twitter-handels that...
# ...are in the basis data set (nobody outside the candidate's realm)
edgs03 <- edgs00 %>%
  unique(.)

# creating the final graph
grph03 <- graph_from_data_frame(edgs03,
                                directed = TRUE,
                                vertices = vert00)

## Analyzing number of links and building adjecency matrix
# getting descriptive values of number of links
deg00 <- grph03 %>% 
  degree(.)
summary(deg00)

# crating the adjecency matrix
adjmat00 <- grph03 %>% 
  as_adjacency_matrix(.)

# getting dimensions of adjecency matrix
dim(adjmat00)


## saving results and removing auxillary variables
# saving results
adjmat00 %>%
  `colnames<-`(NULL) %>% # getting rid of column names
   write.matrix(., file = "D:/Studium/MT_MasterThesis/MT_Code/NetLogo_Code/Data/test_adj_matx01.txt")

vert00$name %>%
  unique(.) %>%
  saveRDS(., file = "./DataFrames/namestring_nwmembers00.rds")


## removing auxillary variables
rm(list= ls(pattern= "data"))
rm(list= ls(pattern= "edgs"))
rm(list= ls(pattern= "grph"))
rm(list= ls(pattern= "vert"))
rm(list= ls(pattern= "df_"))
rm(list= ls(pattern= "adjmat"))

```

