---
title: "MT Code Result Analysis 09"
author: "Markus Rottmann"
date: "2021 05 23"
output:
  html_document:
      toc: true
      toc_depth: 5
---

****

&nbsp;

#### Description

This Code is to analyze/build the results from the simulating each countermeasure (in NetLogo). It calculates descriptive statistics, renders plots, performs OLSs and performs hypothesis tests. 
<br>

The settings for the simulation runs are:

  + 10 initial information pollution tweets.
  + 7 days of tweet life-span (ip-tweet is not recognized as such after 7 days).
  + 365 days of simulation.

<br>
  
**Input**

  + `network_sim_warn_02_04_noip10_lstwt7_365_01.csv`: Results of simulation runs for countermeasure _warning label_.
  + `network_sim_susp_02_03_noip10_lstwt7_365_01.csv`: Results of simulation runs for countermeasure _account suspension_.
  + `network_sim_ban_02_03_noip10_lstwt7_365_01.csv`: Results of simulation runs for countermeasure _account ban_.

<br>
  
**Output**

  + `ols_warn_noip10_lstwt07_365_real_02.html`: OLS results for real-life network for countermeasure _warning label_.
  + `ols_warn_noip10_lstwt07_365_sim_02.html`: OLS results for artificial networks for countermeasure _warning label_.
  + `plt_warn_noip10_lstwt07_real_allobs_01.png`: plot ip-tweets vs. countermeasure strength of real-life network for countermeasure _warning label_.
  + `plt_warn_noip10_lstwt07_artif_365_01.png`: plot ip-tweets vs. countermeasure strength of artificial networks, only those simulation runs that reach 365 days for countermeasure _warning label_.
  + `plt_warn_noip10_lstwt07_all_allobs_01.png`: plot ip-tweets vs. countermeasure strength of all networks and all runs for countermeasure _warning label_.
  + `ols_susp_noip10_lstwt07_365_real_02.html`: OLS results for real-life network for countermeasure _account suspension_.
  + `ols_susp_noip10_lstwt07_365_sim_02.html`: OLS results for artificial networks for countermeasure _account suspension_.
  + `plt_susp_noip10_lstwt07_real_allobs_01.png`: plot ip-tweets vs. countermeasure strength of real-life network for countermeasure _account suspension_.
  + `plt_susp_noip10_lstwt07_artif_365_01.png`: plot ip-tweets vs. countermeasure strength of artificial networks, only those simulation runs that reach 365 days for countermeasure _account suspension_.
  + `plt_susp_noip10_lstwt07_all_allobs_01.png`: plot ip-tweets vs. countermeasure strength of all networks and all runs for countermeasure _account suspension_.
  + `ols_ban_noip10_lstwt07_365_real_02.html`: OLS results for real-life network for countermeasure _account ban_.
  + `ols_ban_noip10_lstwt07_365_sim_02.html`: OLS results for artificial networks for countermeasure _account ban_.
  + `plt_ban_noip10_lstwt07_real_allobs_01.png`: plot ip-tweets vs. countermeasure strength of real-life network for countermeasure _account ban_.
  + `plt_ban_noip10_lstwt07_artif_365_01.png`: plot ip-tweets vs. countermeasure strength of artificial networks, only those simulation runs that reach 365 days for countermeasure _account ban_.
  + `plt_ban_noip10_lstwt07_all_allobs_01.png`: plot ip-tweets vs. countermeasure strength of all networks and all runs for countermeasure _account ban_.




```{r setup, include = TRUE, results = FALSE, warning = FALSE, message = FALSE}

## clearing memory
rm(list=ls(all=T))

## loading (and installing) packages
# defining required packages
req_packages <- c("dplyr", "knitr", "kableExtra", "rvest", "igraph",
"ggplot2", "tibble", "quanteda", "stargazer", "tidyr", "stringr", "lme4",
"rtweet", "lubridate", "MASS", "dplyr", "lsmeans")

# checking, if already installed
new_packages <- req_packages[!(req_packages %in% installed.packages()[,"Package"])]

# installing (downloading) missing packages
if(length(new_packages) > 0) {
  install.packages(new_packages)
} 

# loading required packages
lapply(req_packages, library, character.only = TRUE) 

# deleting auxillary variables
rm(req_packages, new_packages)

## setting global options
options(repos = "https://cran.rstudio.com")
options(stringsAsFactors = FALSE)
knitr::opts_chunk$set(echo = TRUE, fig.width = 7, fig.height = 5)


# frequenty needed packages: ("dplyr", "knitr", "kableExtra", "rvest", "igraph",
# "pageviews", "WikipediR", "ggplot2", "tibble", "quanteda", "stargazer", "tidyr",
# "stringr", "lme4", "rtweet", "lubridate")


```


&nbsp;

***

#### 1. Contermeasure "Warning"

16 x ~20 Runs are performed. Settings for these simulation runs are:

  + Real-life network with 858 members, average node density = 30
    - Run 1: 0% lowering of probability to post an IP Tweet.
    - Run 2: 25% lowering of probability to post an IP Tweet.
    - Run 3: 50% lowering of probability to post an IP Tweet.
    - Run 4: 75% lowering of probability to post an IP Tweet.

  + Simulated Network with 858 members, average node density = 15
    - Run 1: 0% lowering of probability to post an IP Tweet.
    - Run 2: 25% lowering of probability to post an IP Tweet.
    - Run 3: 50% lowering of probability to post an IP Tweet.
    - Run 4: 75% lowering of probability to post an IP Tweet.

  + Simulated Network with 858 members, average node density = 30
    - Run 1: 0% lowering of probability to post an IP Tweet.
    - Run 2: 25% lowering of probability to post an IP Tweet.
    - Run 3: 50% lowering of probability to post an IP Tweet.
    - Run 4: 75% lowering of probability to post an IP Tweet.

  + Simulated Network with 858 members, average node density = 45
    - Run 1: 0% lowering of probability to post an IP Tweet.
    - Run 2: 25% lowering of probability to post an IP Tweet.
    - Run 3: 50% lowering of probability to post an IP Tweet.
    - Run 4: 75% lowering of probability to post an IP Tweet.

<br>
    
##### 1.1 Data Preparation

```{r 01_01 warning_dataprep, include = TRUE, results = TRUE, eval = TRUE, message = FALSE, warning = FALSE}


#### Loading Data & Preparing data
data00 <- read.csv2(file = "./RawData/network_sim_warn_02_04_noip10_lstwt7_365_01.csv") %>%
  `colnames<-`(c("p_warn", "dens", "descr", "val"))

## Brining data in wide format, adding ticks and turtles to same observation ---------------
# getting number of rows
n_row <- nrow(data00) # number of rows
# making vector with run-ids (3 values per run)
vct00 <- rep(x = (1:(n_row/3)) , times = 3) %>% 
  as.numeric(.) %>% 
  sort(.)
# attaching vector to data00 and spread (from long to wide format)
data01 <- data00 %>% 
  cbind(., run_id = vct00) %>% 
  spread(., key = c("descr"), value = "val") %>% 
  dplyr::select(., run_id, p_warn, dens, sum_newip, sum_trltls, ticks)
# saving wide format observations
data01 %>% 
   saveRDS(., file = "./RawData/nw_sim_warn_noip10_ls7_356_wide_01.RDS")

## First Plot of Results "Warning"
# with all observations (including those stopping before 365 days)
data02 <- data01 %>%
          group_by(p_warn, dens) %>% 
          summarize(mn_newip = mean(sum_newip), sd_newip = sd(sum_newip))
# only observatons that ran to 365 days
data03 <- data01 %>%
          filter(., ticks == 365) %>% 
          group_by(p_warn, dens) %>% 
          summarize(mn_newip = mean(sum_newip), sd_newip = sd(sum_newip))

```
<br>

##### 1.2 Descriptive and OLS

```{r 01_02 warning_OLS, include = TRUE, results = FALSE, eval = TRUE, message = FALSE, warning = FALSE}

#### calculating Descriptive -------------------------------------------------------------------
## Numbers of ticks for all rounds
# calculating
res_d00 <- data01 %>% 
  group_by(., p_warn, dens) %>% 
  summarize(mean = mean(ticks))
# showing
res_d00

#### performing OLS -------------------------------------------------------------------

## for network density "real" ----------
# all observations
res01a <- data01 %>% 
         filter(., dens %in% "real") %>% 
         lm(data = ., formula = sum_newip ~ p_warn)
summary(res01a)

# observations that ran for 365 days
res01b <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "real") %>% 
         lm(data = ., formula = sum_newip ~ p_warn)
summary(res01b)

# observations that ran for 365 days & between point 0 & 1
res01b_0_1 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "real") %>%
         filter(., p_warn == 0 | p_warn == 25) %>% 
         lm(data = ., formula = sum_newip ~ p_warn)
summary(res01b_0_1)

# observations that ran for 365 days & between point 1 & 2
res01b_1_2 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "real") %>%
         filter(., p_warn == 25 | p_warn == 50) %>% 
         lm(data = ., formula = sum_newip ~ p_warn)
summary(res01b_1_2)

# # observations that ran for 365 days & between point 0 & 2
res01b_0_2 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "real") %>% 
         filter(., p_warn == 0 | p_warn == 25 | p_warn == 50) %>% 
         lm(data = ., formula = sum_newip ~ p_warn)
summary(res01b_0_2)


## for network density "sim_15" ----------
# all observations
res02a <- data01 %>% 
         filter(., dens %in% "sim_15") %>% 
         lm(data = ., formula = sum_newip ~ p_warn)
summary(res02a)

# observations that ran for 365 days
res02b <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_15") %>% 
         lm(data = ., formula = sum_newip ~ p_warn)
summary(res02b)

# observations that ran for 365 days & between point 0 & 1
res02b_0_1 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_15") %>%
         filter(., p_warn == 0 | p_warn == 25) %>% 
         lm(data = ., formula = sum_newip ~ p_warn)
summary(res02b_0_1)


## for network density "sim_30" ----------
# all observations
res03a <- data01 %>% 
         filter(., dens %in% "sim_30") %>% 
         lm(data = ., formula = sum_newip ~ p_warn)
summary(res03a)

# observations that ran for 365 days
res03b <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_30") %>% 
         lm(data = ., formula = sum_newip ~ p_warn)
summary(res03b)

# observations that ran for 365 days & between point 0 & 1
res03b_0_1 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_30") %>%
         filter(., p_warn == 0 | p_warn == 25) %>% 
         lm(data = ., formula = sum_newip ~ p_warn)
summary(res03b_0_1)

# observations that ran for 365 days & between point 1 & 2
res03b_1_2 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_30") %>%
         filter(., p_warn == 25 | p_warn == 50) %>% 
         lm(data = ., formula = sum_newip ~ p_warn)
summary(res03b_1_2)

# # observations that ran for 365 days & between point 0 & 2
res03b_0_2 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_30") %>% 
         filter(., p_warn == 0 | p_warn == 25 | p_warn == 50) %>% 
         lm(data = ., formula = sum_newip ~ p_warn)
summary(res03b_0_2)

## for network density "sim_45" ----------
# all observations
res04a <- data01 %>% 
         filter(., dens %in% "sim_45") %>% 
         lm(data = ., formula = sum_newip ~ p_warn)
summary(res04a)

# observations that ran for 365 days
res04b <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_45") %>% 
         lm(data = ., formula = sum_newip ~ p_warn)
summary(res04b)

# observations that ran for 365 days & between point 0 & 1
res04b_0_1 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_45") %>%
         filter(., p_warn == 0 | p_warn == 25) %>% 
         lm(data = ., formula = sum_newip ~ p_warn)
summary(res04b_0_1)

# observations that ran for 365 days & between point 1 & 2
res04b_1_2 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_45") %>%
         filter(., p_warn == 25 | p_warn == 50) %>% 
         lm(data = ., formula = sum_newip ~ p_warn)
summary(res04b_1_2)

# observations that ran for 365 days & between point 0 & 2
res04b_0_2 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_45") %>% 
         filter(., p_warn == 0 | p_warn == 25 | p_warn == 50) %>% 
         lm(data = ., formula = sum_newip ~ p_warn)
summary(res04b_0_2)


#### saving results
## "real", observations that ran 365 days
# defining column labels
col_lab = c("0% up to 25%", "25% up to 50%", "0% up to 50%")
# rendering and saving regression table
stargazer(res01b_0_1, res01b_1_2, res01b_0_2,
         column.labels = col_lab,
         title = "Countermeasure Warning",
         style = "apsr",
         digits = 2,
         type = "html",
         out = "./PlotsTables/ols_warn_noip10_lstwt07_365_real_02.html")

## All models, observations that ran 365 days
# defining column labels
col_lab = c("Sim 15: 0-25", 
            "Sim 30: 0-25", "Sim 30: 25-50", "Sim 30: 0 - 50",
            "Sim 45: 0-25", "Sim 45: 25-50", "Sim 45: 0 - 50",
            "Real: 0-25", "Real: 25-50", "Real: 0 - 50")
# rendering and saving regression table
stargazer(res02b_0_1, 
         res03b_0_1, res03b_1_2, res03b_0_2,
         res04b_0_1, res04b_1_2, res04b_0_2,
         res01b_0_1, res01b_1_2, res01b_0_2,
         column.labels = col_lab,
         title = "Countermeasure Warning",
         style = "apsr",
         digits = 2,
         type = "html",
         out = "./PlotsTables/ols_warn_noip10_lstwt07_365_sim_02.html")

##### Calculating Descritpive Stuff ----------------------------------------------

# Getting Summaries
res05 <- data01 %>% 
         filter(., dens %in% "sim_30") %>% 
         filter(., p_warn == 50) %>% 
         dplyr::select(., ticks) %>% 
         summary(.)
# res05

# Getting Number Runs wrt. reaching 365 days
res06 <- data01 %>% 
         filter(., dens %in% "sim_15") %>% 
         filter(., p_warn == 25) %>% 
         dplyr::select(., ticks) %>% 
         arrange(desc(ticks))
# res06


####### Doing Hypotheses Tests for [H2a] ----------------------------------------------

#### For Real-World Network
# for portion 0% to 25%
int_res01b_0_1 <- res01b_0_1 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res01b_0_1 <-  int_res01b_0_1[2, "Estimate"]
se_res01b_0_1 <- int_res01b_0_1[2, "Std. Error"]

# for portion 25% to 50%
int_res01b_1_2 <- res01b_1_2 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res01b_1_2 <-  int_res01b_1_2[2, "Estimate"]
se_res01b_1_2 <- int_res01b_1_2[2, "Std. Error"]

# calculation Z-Value & getting p-value
z_res01b_0_2 <- (b_res01b_1_2 - b_res01b_0_1)/sqrt( (se_res01b_0_1)^2 + (se_res01b_1_2)^2 ) 
p_res01b_0_2 <- pnorm(q = z_res01b_0_2, lower.tail = TRUE)
p_res01b_0_2 

#### For for network density "sim_15" 
# for portion 0% to 25%
int_res02b_0_1 <- res02b_0_1 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res02b_0_1 <-  int_res02b_0_1[2, "Estimate"]
se_res02b_0_1 <- int_res02b_0_1[2, "Std. Error"]


#### For for network density "sim_30" 
# for portion 0% to 25%
int_res03b_0_1 <- res03b_0_1 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res03b_0_1 <-  int_res03b_0_1[2, "Estimate"]
se_res03b_0_1 <- int_res03b_0_1[2, "Std. Error"]

# for portion 25% to 50%
int_res03b_1_2 <- res03b_1_2 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res03b_1_2 <-  int_res03b_1_2[2, "Estimate"]
se_res03b_1_2 <- int_res03b_1_2[2, "Std. Error"]

# calculation Z-Value & getting p-value
z_res03b_0_2 <- (b_res03b_1_2 - b_res03b_0_1)/sqrt( (se_res03b_0_1)^2 + (se_res03b_1_2)^2 ) 
p_res03b_0_2 <- pnorm(q = z_res03b_0_2, lower.tail = TRUE)
p_res03b_0_2 


#### For for network density "sim_45" 
# for portion 0% to 25%
int_res04b_0_1 <- res04b_0_1 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res04b_0_1 <-  int_res04b_0_1[2, "Estimate"]
se_res04b_0_1 <- int_res04b_0_1[2, "Std. Error"]

# for portion 25% to 50%
int_res04b_1_2 <- res04b_1_2 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res04b_1_2 <-  int_res04b_1_2[2, "Estimate"]
se_res04b_1_2 <- int_res04b_1_2[2, "Std. Error"]

# calculation Z-Value & getting p-value
z_res04b_0_2 <- (b_res04b_1_2 - b_res04b_0_1)/sqrt( (se_res04b_0_1)^2 + (se_res04b_1_2)^2 ) 
p_res04b_0_2 <- pnorm(q = z_res04b_0_2, lower.tail = TRUE)
p_res04b_0_2 


## preparing and displaying result data frame
# preparing result data frame
h_test00 <- data.frame(Network = c("Real-World: Diff. Effect",
                                 "Real-World: p-Value",
                                 
                                 "Art. 15: Diff. Effect",
                                 "Art. 15: p-Value",
                                 
                                 "Art. 30: Diff. Effect",
                                 "Art. 30: p-Value",
                                 
                                 "Art. 45: Diff. Effect",
                                 "Art. 45: p-Value"),
                     
                     "0% - 25% vs. 25% - 50%" = c((b_res01b_1_2 - b_res01b_0_1), # real-world
                                                p_res01b_0_2,
                                                
                                                NA,                              # artificial 15
                                                NA,
                                                
                                                (b_res03b_1_2 - b_res03b_0_1),   # artificial 30
                                                p_res03b_0_2,
                                                  
                                                (b_res04b_1_2 - b_res04b_0_1),   # artificial 45
                                                p_res04b_0_2),
                     
                     
                     "25% - 50% vs. 50% - 75%" = c(NA, # real-world
                                                 NA,
                     
                                                 NA,   # artificial 15
                                                 NA,
                                                 
                                                 NA,   # artificial 30
                                                 NA,  
                                                 
                                                 NA,   # artificial 45
                                                 NA)
              ) %>% 
  `colnames<-`(c("Network", "0% - 25% vs. 25% - 50%", "25% - 50% vs. 50% - 75%")) 


# displaying hypothesis test table
h_test00%>% kable(.)



####### Doing Hypotheses Tests for [H3] ----------------------------------------------
## NOTE: I take advantage that coeficients and standard errors are already defined

## Art. 15 vs. Art. 30
# Portion 0% to 25%
z_res0203_0_1 <- (b_res02b_0_1 - b_res03b_0_1)/sqrt( (se_res02b_0_1)^2 + (se_res03b_0_1)^2 ) 
p_res0203_0_1 <- pnorm(q = z_res0203_0_1, lower.tail = TRUE)
p_res0203_0_1

# Portion 25% to 50%
# NA

# Portion 50% to 75%
# NA


## Art. 30 vs. Art. 45
# Portion 0% to 25%
z_res0304_0_1 <- (b_res03b_0_1 - b_res04b_0_1)/sqrt( (se_res03b_0_1)^2 + (se_res04b_0_1)^2 ) 
p_res0304_0_1 <- pnorm(q = z_res0304_0_1, lower.tail = TRUE)
p_res0304_0_1

# Portion 25% to 50%
z_res0304_1_2 <- (b_res03b_1_2 - b_res04b_1_2)/sqrt( (se_res03b_1_2)^2 + (se_res04b_1_2)^2 ) 
p_res0304_1_2 <- pnorm(q = z_res0304_1_2, lower.tail = TRUE)
p_res0304_1_2

# Portion 50% to 75%
# NA


## Producing and Displaying Table of Results
# preparing data frame
h_test01 <- data.frame(Network = c("0% - 25%: Diff. Effect",
                                   "0% - 25%: p-Value",

                                   "25% - 50%: Diff. Effect",
                                   "25% - 50%: p-Value",

                                   "50% - 75%: Diff. Effect",
                                   "50% - 75%: p-Value"),

                     "Art. 15 vs. Art. 30" = c((b_res03b_0_1 - b_res02b_0_1), 
                                                p_res0203_0_1,

                                                NA,                          
                                                NA,
                                               
                                                NA,
                                                NA),


                     "Art. 20 vs. Art. 45"     = c((b_res04b_0_1 - b_res03b_0_1),
                                                 p_res0304_0_1,

                                                 c((b_res04b_1_2 - b_res03b_1_2),  
                                                 p_res0304_1_2,

                                                 NA,  
                                                 NA))) %>%
  
`colnames<-`(c("Network", "Art. 15 vs. Art. 30", "Art. 20 vs. Art. 45"))

# displaying data frame
h_test01%>% kable(.)

```
<br>

##### 1.3 Plots

```{r 01_03 warning_Plots, include = TRUE, results = TRUE, eval = TRUE, message = FALSE, warning = FALSE}


#### creating plots -----------------------------------------------------------------

## "Real-Life" Network Only (365 and All) ---------------
# Preparing Data
data04 <- data02 %>% 
  filter(., dens %in% "real") %>% 
  filter(., p_warn >= 50) %>% 
  mutate(., dat_bas = "all")
data05 <- data03 %>% 
  filter(., dens %in% "real") %>% 
  mutate(., dat_bas = "365_oly")
data06 <- data04 %>% 
  rbind(., data05)

## rendering, showing and saving plot
# rendering
gg01 <- data06 %>%
        ggplot( aes(x = p_warn, 
                    group = dat_bas,
                    color = dat_bas) ) +
  
        geom_line(aes(y = mn_newip ),
                  size = 1.0) +
  
        geom_errorbar(aes(ymin = mn_newip - sd_newip,
                      ymax = mn_newip + sd_newip),
                      colour = "black",
                      width = 2.0,
                      size = 0.5) +
  
        geom_point(aes(y = mn_newip),
                   size = 1.5) +

        scale_y_continuous(name ="Information Pollution Tweets [--]",
                           limits = c(-50, 3550)) +
  
        scale_x_continuous(name = "Probability Lowered [%]",
                           breaks = c(0, 25, 50, 75),
                           limits = c(-1, 76)) +

        scale_color_grey(name = "Runs:",
                         labels = c("365 days", "Less than\n365 days")) +

        theme_bw()

# saving
gg01 %>% 
  ggsave(., filename = "./PlotsTables/plt_warn_noip10_lstwt07_real_allobs_01.png",
      units = "cm",
      dpi = "retina",
      height = 8,
      width = 14)


#### "Artificial Network" 365 days Only ---------------------------------------
# rendering
gg02 <- data03 %>%
  
        filter(., dens %in% c("sim_15", "sim_30", "sim_45")) %>%  
  
        ggplot( aes(x = p_warn,
                    group = dens,
                    color = dens) ) +
  
        geom_line(aes(y = mn_newip ),
                      size = 1.0) +
  
        geom_errorbar(aes(ymin = mn_newip - sd_newip,
                          ymax = mn_newip + sd_newip),
                          colour = "black",
                          width = 2.0,
                          size = 0.5) +
  
        geom_point(aes(y = mn_newip),
                       size = 1.5) +

        scale_y_continuous(name ="Information Pollution Tweets [--]",
                           limits = c(-50, 5100)) +

        scale_x_continuous(name = "Probability Lowered [%]",
                           breaks = c(0, 25, 50, 75),
                           limits = c(-1, 76)) +
  
        scale_color_grey(name = "Density:",
                         labels = c("15 links", "30 links", "45 links")) +

        theme_bw()

# showing plot
gg02
# saving plot
gg02 %>% 
  ggsave(., filename = "./PlotsTables/plt_warn_noip10_lstwt07_artif_365_01.png",
      units = "cm",
      dpi = "retina",
      height = 8,
      width = 14)


#### Real and Artificial Networks, All Observations ---------------------------------------
# rendering
gg03 <- data02 %>%
  
        ggplot( aes(x = p_warn,
                    group = dens,
                    color = dens) ) +
  
        geom_line(aes(y = mn_newip ),
                      size = 1.0) +
  
        geom_errorbar(aes(ymin = mn_newip - sd_newip,
                          ymax = mn_newip + sd_newip),
                          colour = "black",
                          width = 1.75,
                          size = 0.5) +
  
        geom_point(aes(y = mn_newip),
                       size = 1.5) +

        scale_y_continuous(name ="Information Pollution Tweets [--]",
                           limits = c(-50, 5100)) +

        scale_x_continuous(name = "Probability Lowered [%]",
                           breaks = c(0, 25, 50, 75),
                           limits = c(-1, 76)) +
  
        scale_color_grey(name = "Network:",
                         labels = c("Real 30", "Artif. 15", "Artif. 30", "Artif. 45")) +

        theme_bw()

# showing plot
gg03

# saving plot
gg03 %>% 
  ggsave(., filename = "./PlotsTables/plt_warn_noip10_lstwt07_all_allobs_01.png",
      units = "cm",
      dpi = "retina",
      height = 8,
      width = 14)

#### Cleanup --------------------------------------------------------------------------------------
## removing auxillary variables
rm(col_lab, n_row)
rm(list = ls(pattern = "data"))
rm(list = ls(pattern = "int_"))
rm(list = ls(pattern = "vct"))
rm(list = ls(pattern = "res"))
rm(list = ls(pattern = "gg"))


```


&nbsp;

***

#### 2. Contermeasure "Account Suspension"

16 x ~20 Runs are performed. Settings for these simulation runs are:

  + Real-life Network with 858 members, average node density = 30
    - Run 1: suspending the account for 0 days.
    - Run 2: suspending the account for 2 days (IP-tweet remains invisible).
    - Run 3: suspending the account for 4 days (IP-tweet remains invisible).
    - Run 4: suspending the account for 6 days (IP-tweet remains invisible).
 
  + Simulated Network with 858 members, average node density = 15
    - Run 1: suspending the account for 0 days.
    - Run 2: suspending the account for 2 days (IP-tweet remains invisible).
    - Run 3: suspending the account for 4 days (IP-tweet remains invisible).
    - Run 4: suspending the account for 6 days (IP-tweet remains invisible).
    
  + Simulated Network with 858 members, average node density = 30
    - Run 1: suspending the account for 0 days.
    - Run 2: suspending the account for 2 days (IP-tweet remains invisible).
    - Run 3: suspending the account for 4 days (IP-tweet remains invisible).
    - Run 4: suspending the account for 6 days (IP-tweet remains invisible).
    
  + Simulated Network with 858 members, average node density = 45
    - Run 1: suspending the account for 0 days.
    - Run 2: suspending the account for 2 days (IP-tweet remains invisible).
    - Run 3: suspending the account for 4 days (IP-tweet remains invisible).
    - Run 4: suspending the account for 6 days (IP-tweet remains invisible).

<br>


##### 2.1 Data Preparation

```{r 02_01 suspension_dataprep, include = TRUE, results = TRUE, eval = TRUE, message = FALSE, warning = FALSE}

## Loading Data
data00 <- read.csv2(file = "./RawData/network_sim_susp_02_03_noip10_lstwt7_365_01.csv") %>%
  `colnames<-`(c("no_sus", "dens", "descr", "val"))


## Brining data in wide format, adding ticks and turtles to same observation
# getting number of rows
n_row <- nrow(data00) # number of rows
# making vector with run-ids (3 values per run)
vct00 <- rep(x = (1:(n_row/3)) , times = 3) %>% 
  as.numeric(.) %>% 
  sort(.)
# attaching vector to data00 and spread (from long to wide format)
data01 <- data00 %>% 
  cbind(., run_id = vct00) %>% 
  spread(., key = c("descr"), value = "val") %>% 
  dplyr::select(., run_id, no_sus, dens, sum_newip, sum_trltls, ticks)
# saving wide format observations
data01 %>% 
   saveRDS(., file = "./RawData/nw_sim_sus_noip10_ls7_356_wide_01.RDS")

## First Plot of Results "Warning"
# with all observations (including those stopping before 365 days)
data02 <- data01 %>%
          group_by(no_sus, dens) %>% 
          summarize(mn_newip = mean(sum_newip), sd_newip = sd(sum_newip))

# only observatons that ran to 365 days
data03 <- data01 %>%
          filter(., ticks == 365) %>% 
          group_by(no_sus, dens) %>% 
          summarize(mn_newip = mean(sum_newip), sd_newip = sd(sum_newip))
``` 
<br>


##### 2.2 Descriptive and OLS

```{r 02_02 suspension_OLS, include = TRUE, results = TRUE, eval = TRUE, message = FALSE, warning = FALSE}


#### calculating Descriptive -------------------------------------------------------------------

## Numbers of ticks for all rounds
# calculating
res_d00 <- data01 %>% 
  group_by(., no_sus, dens) %>% 
  summarize(mean = mean(ticks))
# showing
res_d00


#### performing OLS ----------------------------------------------

## for network density "real" ----------
# all observations
res01a <- data01 %>% 
         filter(., dens %in% "real") %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res01a)

# observations that ran for 365 days
res01b <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "real") %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res01b)

# observations that ran for 365 days & between point 0 & 1
res01b_0_1 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "real") %>%
         filter(., no_sus == 0 | no_sus == 2) %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res01b_0_1)

# observations that ran for 365 days & between point 1 & 2
res01b_1_2 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "real") %>%
         filter(., no_sus == 2 | no_sus == 4) %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res01b_1_2)

# observations that ran for 365 days & between point 2 & 3
res01b_2_3 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "real") %>%
         filter(., no_sus == 4 | no_sus == 6) %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res01b_2_3)

# # observations that ran for 365 days & between point 0 & 2
res01b_0_3 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "real") %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res01b_0_3)


## for network density "sim_15" ----------
# all observations
res02a <- data01 %>% 
         filter(., dens %in% "sim_15") %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res02a)

# observations that ran for 365 days
res02b <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_15") %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res02b)

# observations that ran for 365 days & between point 0 & 1
res02b_0_1 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_15") %>%
         filter(., no_sus == 0 | no_sus == 2) %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res02b_0_1)


## for network density "sim_30" ----------
# all observations
res03a <- data01 %>% 
         filter(., dens %in% "sim_30") %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res03a)

# observations that ran for 365 days
res03b <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_30") %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res03b)

# observations that ran for 365 days & between point 0 & 1
res03b_0_1 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_30") %>%
         filter(., no_sus == 0 | no_sus == 2) %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res03b_0_1)

# observations that ran for 365 days & between point 1 & 2
res03b_1_2 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_30") %>%
         filter(., no_sus == 2 | no_sus == 4) %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res03b_1_2)

# # observations that ran for 365 days & between point 0 & 2
res03b_0_2 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_30") %>% 
         filter(., no_sus == 0 | no_sus == 2 | no_sus == 4) %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res03b_0_2)

## for network density "sim_45" ----------
# all observations
res04a <- data01 %>% 
         filter(., dens %in% "sim_45") %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res04a)

# observations that ran for 365 days
res04b <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_45") %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res04b)

# observations that ran for 365 days & between point 0 & 1
res04b_0_1 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_45") %>%
         filter(., no_sus == 0 | no_sus == 2) %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res04b_0_1)

# observations that ran for 365 days & between point 1 & 2
res04b_1_2 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_45") %>%
         filter(., no_sus == 2 | no_sus == 4) %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res04b_1_2)

# observations that ran for 365 days & between point 2 & 3
res04b_2_3 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_45") %>%
         filter(., no_sus == 4 | no_sus == 6) %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res04b_2_3)

# observations that ran for 365 days & between point 0 & 2
res04b_0_3 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_45") %>% 
         lm(data = ., formula = sum_newip ~ no_sus)
summary(res04b_0_3)


#### saving results
## "real", observations that ran 365 days
# defining column labels
col_lab = c("0 to 2 days", "2 to 4 days",
            "4 to 6 days", "0 to 6 days")
# rendering and saving regression table
stargazer(res01b_0_1, res01b_1_2,
          res01b_2_3, res01b_0_3,
         column.labels = col_lab,
         title = "Countermeasure Account Suspension",
         style = "apsr",
         digits = 2,
         type = "html",
         out = "./PlotsTables/ols_susp_noip10_lstwt07_365_real_02.html")

## All models, observations that ran 365 days
# defining column labels
col_lab = c("Sim 15: 0-2", 
            "Sim 30: 0-2", "Sim 30: 2-4", "Sim 30: 0-4",
            "Sim 45: 0-2", "Sim 45: 2-4", "Sim 45: 4-6", "Sim 45: 0-6",
            "Real: 0-2", "Real: 2-4", "Real: 4-6", "Real: 0-6")
# rendering and saving regression table
stargazer(res02b_0_1, 
          res03b_0_1, res03b_1_2, res03b_0_2,
          res04b_0_1, res04b_1_2, res04b_2_3, res04b_0_3,
          res01b_0_1, res01b_1_2, res01b_2_3, res01b_0_3,
          column.labels = col_lab,
          title = "Countermeasure Account Suspension",
          style = "apsr",
          digits = 2,
          type = "html",
          out = "./PlotsTables/ols_susp_noip10_lstwt07_365_sim_02.html")

# getting Summaries (various)
res05 <- data01 %>% 
         filter(., dens %in% "sim_30") %>% 
         filter(., no_sus == 4) %>% 
         dplyr::select(., ticks) %>% 
         summary(.)
res05

# getting Survivors (various)
res06 <- data01 %>% 
         filter(., dens %in% "sim_45") %>% 
         filter(., no_sus == 6) %>% 
         arrange(desc(ticks))
res06


####### Doing Hypotheses Tests for [H2b] ----------------------------------------------

#### For Real-World Network
# for portion 0 days to 2 days
int_res01b_0_1 <- res01b_0_1 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res01b_0_1 <-  int_res01b_0_1[2, "Estimate"]
se_res01b_0_1 <- int_res01b_0_1[2, "Std. Error"]

# for portion 2 days to 4 days
int_res01b_1_2 <- res01b_1_2 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res01b_1_2 <-  int_res01b_1_2[2, "Estimate"]
se_res01b_1_2 <- int_res01b_1_2[2, "Std. Error"]

# for portion 4 days to 6 days
int_res01b_2_3 <- res01b_2_3 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res01b_2_3 <-  int_res01b_2_3[2, "Estimate"]
se_res01b_2_3 <- int_res01b_2_3[2, "Std. Error"]

# calculation Z-Value & getting p-value
# portion 0 to 4 days
z_res01b_0_2 <- (b_res01b_1_2 - b_res01b_0_1)/sqrt( (se_res01b_1_2)^2 + (se_res01b_0_1)^2 ) 
p_res01b_0_2 <- pnorm(q = z_res01b_0_2, lower.tail = TRUE)
p_res01b_0_2 

# portion 2 to 6 days
z_res01b_1_3 <- (b_res01b_2_3 - b_res01b_1_2)/sqrt( (se_res01b_2_3)^2 + (se_res01b_1_2)^2 ) 
p_res01b_1_3 <- pnorm(q = z_res01b_1_3, lower.tail = TRUE)
p_res01b_1_3 


#### For for network density "sim_15" 
# for portion 0 days to 2 days
int_res02b_0_1 <- res02b_0_1 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res02b_0_1 <-  int_res02b_0_1[2, "Estimate"]
se_res02b_0_1 <- int_res02b_0_1[2, "Std. Error"]



#### For for network density "sim_30" 
# for portion 0 days to 2 days
int_res03b_0_1 <- res03b_0_1 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res03b_0_1 <-  int_res03b_0_1[2, "Estimate"]
se_res03b_0_1 <- int_res03b_0_1[2, "Std. Error"]

# for portion 2 days to 4 days
int_res03b_1_2 <- res03b_1_2 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res03b_1_2 <-  int_res03b_1_2[2, "Estimate"]
se_res03b_1_2 <- int_res03b_1_2[2, "Std. Error"]

# calculation Z-Value & getting p-value
z_res03b_0_2 <- (b_res03b_1_2 - b_res03b_0_1)/sqrt( (se_res03b_0_1)^2 + (se_res03b_1_2)^2 ) 
p_res03b_0_2 <- pnorm(q = z_res03b_0_2, lower.tail = TRUE)
p_res03b_0_2 


#### For for network density "sim_45" 
### For Real-World Network
# for portion 0 days to 2 days
int_res04b_0_1 <- res04b_0_1 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res04b_0_1 <-  int_res04b_0_1[2, "Estimate"]
se_res04b_0_1 <- int_res04b_0_1[2, "Std. Error"]

# for portion 2 days to 4 days
int_res04b_1_2 <- res04b_1_2 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res04b_1_2 <-  int_res04b_1_2[2, "Estimate"]
se_res04b_1_2 <- int_res04b_1_2[2, "Std. Error"]

# for portion 4 days to 6 days
int_res04b_2_3 <- res04b_2_3 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res04b_2_3 <-  int_res04b_2_3[2, "Estimate"]
se_res04b_2_3 <- int_res04b_2_3[2, "Std. Error"]

# calculation Z-Value & getting p-value
# portion 0 to 4 days
z_res04b_0_2 <- (b_res04b_1_2 - b_res04b_0_1)/sqrt( (se_res04b_1_2)^2 + (se_res04b_0_1)^2 ) 
p_res04b_0_2 <- pnorm(q = z_res04b_0_2, lower.tail = TRUE)
p_res04b_0_2 

# portion 2 to 6 days
z_res04b_1_3 <- (b_res04b_2_3 - b_res04b_1_2)/sqrt( (se_res04b_2_3)^2 + (se_res04b_1_2)^2 ) 
p_res04b_1_3 <- pnorm(q = z_res04b_1_3, lower.tail = TRUE)
p_res04b_1_3 


## preparing and displaying result data frame
# preparing result data frame
h_test00 <- data.frame(Network = c("Real-World: Diff. Effect",
                                 "Real-World: p-Value",
                                 
                                 "Art. 15: Diff. Effect",
                                 "Art. 15: p-Value",
                                 
                                 "Art. 30: Diff. Effect",
                                 "Art. 30: p-Value",
                                 
                                 "Art. 45: Diff. Effect",
                                 "Art. 45: p-Value"),
                     
                     "0 days - 2 days vs. 2 days - 4 days" = c((b_res01b_1_2 - b_res01b_0_1), # real-world
                                                p_res01b_0_2,
                                                
                                                NA,                              # artificial 15
                                                NA,
                                                
                                                (b_res03b_1_2 - b_res03b_0_1),   # artificial 30
                                                p_res03b_0_2,
                                                  
                                                (b_res04b_1_2 - b_res04b_0_1),   # artificial 45
                                                p_res04b_0_2),
                     
                     
                     "2 days - 4 days vs. 4 days - 6 days" = c((b_res01b_2_3 - b_res01b_1_2), # real-world
                                                p_res01b_1_3,
                     
                                                 NA,   # artificial 15
                                                 NA,
                                                 
                                                 NA,   # artificial 30
                                                 NA,  
                                                 
                                                (b_res04b_2_3 - b_res04b_1_2),   # artificial 45
                                                p_res04b_1_3)
              ) %>% 
  
  `colnames<-`(c("Network",
                 "0 days - 2 days vs. 2 days - 4 days",
                 "2 days - 4 days vs. 4 days - 6 days"))

# displaying hypothesis test table
h_test00 %>% kable(.)


####### Doing Hypotheses Tests for [H3] ----------------------------------------------
## NOTE: I take advantage that coeficients and standard errors are already defined

## Art. 15 vs. Art. 30
# Portion 0 days to 2 days
z_res0203_0_1 <- (b_res02b_0_1 - b_res03b_0_1)/sqrt( (se_res02b_0_1)^2 + (se_res03b_0_1)^2 ) 
p_res0203_0_1 <- pnorm(q = z_res0203_0_1, lower.tail = TRUE)
p_res0203_0_1

# Portion 2 days to 4 days
# NA

# Portion 4 days to 6 days
# NA


## Art. 30 vs. Art. 45
# Portion 0 days to 2 days
z_res0304_0_1 <- (b_res03b_0_1 - b_res04b_0_1)/sqrt( (se_res03b_0_1)^2 + (se_res04b_0_1)^2 ) 
p_res0304_0_1 <- pnorm(q = z_res0304_0_1, lower.tail = TRUE)
p_res0304_0_1

# Portion 2 days to 4 days
z_res0304_1_2 <- (b_res03b_1_2 - b_res04b_1_2)/sqrt( (se_res03b_1_2)^2 + (se_res04b_1_2)^2 ) 
p_res0304_1_2 <- pnorm(q = z_res0304_1_2, lower.tail = TRUE)
p_res0304_1_2

# Portion 4 days to 6 days
# NA


## preparing and displaying data frame
# preparing data frame result data frame
h_test01 <- data.frame(Network = c("0 days - 2 days: Diff. Effect",
                                   "0 days - 2 days: p-Value",

                                   "2 days - 4 days: Diff. Effect",
                                   "2 days - 4 days: p-Value",

                                   "4 days - 6 days: Diff. Effect",
                                   "4 days - 6 days: p-Value"),

                     "Art. 15 vs. Art. 30" = c((b_res03b_0_1 - b_res02b_0_1), 
                                                p_res0203_0_1,

                                                NA,                          
                                                NA,
                                               
                                                NA,
                                                NA),


                     "Art. 30 vs. Art. 45"     = c((b_res04b_0_1 - b_res03b_0_1),
                                                 p_res0304_0_1,

                                                 c((b_res04b_1_2 - b_res03b_1_2),  
                                                 p_res0304_1_2,

                                                 NA,  
                                                 NA))) %>%
  
`colnames<-`(c("Network", "Art. 15 vs. Art. 30", "Art. 30 vs. Art. 45"))

# displaying result data frame
h_test01%>% kable(.)

``` 
<br>


##### 2.3 Plots

```{r 02_03 suspension_plots, include = TRUE, results = TRUE, eval = TRUE, message = FALSE, warning = FALSE}

#### "Real-Life" Network Only ---------------------------------------
# Preparing Data
data04 <- data02 %>% 
  filter(., dens %in% "real") %>% 
  filter(., no_sus >= 4) %>% 
  mutate(., dat_bas = "all")
data05 <- data03 %>% 
  filter(., dens %in% "real") %>% 
  mutate(., dat_bas = "365_oly")
data06 <- data04 %>% 
  rbind(., data05)

# rendering, showing and saving plot
gg01 <- data06 %>%
        ggplot( aes(x = no_sus, 
                    group = dat_bas,
                    color = dat_bas) ) +
  
        geom_line(aes(y = mn_newip ),
                      size = 1.0) +
  
        geom_errorbar(aes(ymin = mn_newip - sd_newip,
                          ymax = mn_newip + sd_newip),
                          colour = "black",
                          width = 0.1,
                          size = 0.5) +
  
        geom_point(aes(y = mn_newip),
                       size = 1.5) +

        scale_y_continuous(name ="Information Pollution Tweets [--]",
                           limits = c(-50, 3550)) +
  
        scale_x_continuous(name = "Days Suspended [d]",
                           breaks = c(0, 2, 4, 6),
                           limits = c(-1, 7)) +
  
        scale_color_grey(name = "Runs:",
                         labels = c("365 days", "Less than\n365 days")) +
  
        theme_bw()

# showing plot
gg01
# saving plot
gg01 %>% 
  ggsave(., filename = "./PlotsTables/plt_susp_noip10_lstwt07_real_allobs_01.png",
      units = "cm",
      dpi = "retina",
      height = 8,
      width = 14)



#### "Artificial Network" 365 days Only ---------------------------------------
# rendering
gg02 <- data03 %>%
  
        filter(., dens %in% c("sim_15", "sim_30", "sim_45")) %>%  
  
        ggplot( aes(x = no_sus,
                    group = dens,
                    color = dens) ) +
  
        geom_line(aes(y = mn_newip ),
                      size = 1.0) +
  
        geom_errorbar(aes(ymin = mn_newip - sd_newip,
                          ymax = mn_newip + sd_newip),
                          colour = "black",
                          width = 0.1,
                          size = 0.5) +
  
        geom_point(aes(y = mn_newip),
                       size = 1.5) +

        scale_y_continuous(name ="Information Pollution Tweets [--]",
                           limits = c(-50, 5100)) +

        scale_x_continuous(name = "Days of Account Suspension [d]",
                           breaks = c(0, 2, 4, 6),
                           limits = c(-1, 7)) +
  
        scale_color_grey(name = "Density:",
                         labels = c("15 links", "30 links", "45 links")) +

        theme_bw()

# showing plot
gg02
# saving plot
gg02 %>% 
  ggsave(., filename = "./PlotsTables/plt_susp_noip10_lstwt07_artif_365_01.png",
      units = "cm",
      dpi = "retina",
      height = 8,
      width = 14)


#### Real and Artificial Networks, All Observations ---------------------------------------
# rendering
gg03 <- data02 %>%
  
        ggplot( aes(x = no_sus,
                    group = dens,
                    color = dens) ) +
  
        geom_line(aes(y = mn_newip ),
                      size = 1.0) +
  
        geom_errorbar(aes(ymin = mn_newip - sd_newip,
                          ymax = mn_newip + sd_newip),
                          colour = "black",
                          width = 0.1,
                          size = 0.5) +
  
        geom_point(aes(y = mn_newip),
                       size = 1.5) +

        scale_y_continuous(name ="Information Pollution Tweets [--]",
                           limits = c(-50, 5100)) +

        scale_x_continuous(name = "Days of Account Suspension [d]",
                           breaks = c(0, 2, 4, 6),
                           limits = c(-1, 7)) +
  
        scale_color_grey(name = "Network:",
                         labels = c("Real 30", "Artif. 15", "Artif. 30", "Artif. 45")) +

        theme_bw()

# showing plot
gg03

# saving plot
gg03 %>% 
  ggsave(., filename = "./PlotsTables/plt_susp_noip10_lstwt07_all_allobs_01.png",
      units = "cm",
      dpi = "retina",
      height = 8,
      width = 14)


## removing auxillary variables
rm(col_lab, n_row)
rm(list= ls(pattern= "data"))
rm(list= ls(pattern= "vct"))
rm(list= ls(pattern= "res"))
rm(list= ls(pattern= "gg"))

```


&nbsp;

***

#### 3. Contermeasure "Account Ban"

16 x ~20 Runs are performed. Settings for these simulation runs are:

    
  + Real-life Network with 858 members, average node density = 30
    - Run 1: banning 0 accounts.
    - Run 2: banning 91 accounts (one every 4 days).
    - Run 3: banning 183 accounts (one every 2 days).
    - Run 4: banning 273 accounts (one every 36 hours).

  + Simulated Network with 858 members, average node density = 15
    - Run 1: banning 0 accounts.
    - Run 2: banning 91 accounts (one every 4 days).
    - Run 3: banning 183 accounts (one every 2 days).
    - Run 4: banning 273 accounts (one every 36 hours).

  + Simulated Network with 858 members, average node density = 30
    - Run 1: banning 0 accounts.
    - Run 2: banning 91 accounts (one every 4 days).
    - Run 3: banning 183 accounts (one every 2 days).
    - Run 4: banning 273 accounts (one every 36 hours).

  + Simulated Network with 858 members, average node density = 45
    - Run 1: banning 0 accounts.
    - Run 2: banning 91 accounts (one every 4 days).
    - Run 3: banning 183 accounts (one every 2 days).
    - Run 4: banning 273 accounts (one every 36 hours).
    
<br>

##### 3.1 Data Preparation

```{r 03_01 ban_dataprep, include = TRUE, results = TRUE, eval = TRUE, message = FALSE, warning = FALSE}

#### Loading Data
data00 <- read.csv2(file = "./RawData/network_sim_ban_02_03_noip10_lstwt7_365_02.csv") %>%
   dplyr::select(., "..strg", dens, dscr, val) %>% 
  `colnames<-`(c("no_del", "dens", "descr", "val"))


## Brining data in wide format, adding ticks and turtles to same observation
# getting number of rows
n_row <- nrow(data00) # number of rows
# making vector with run-ids (3 values per run)
vct00 <- rep(x = (1:(n_row/3)) , times = 3) %>% 
  as.numeric(.) %>% 
  sort(.)
# attaching vector to data00 and spread (from long to wide format)
data01 <- data00 %>% 
  cbind(., run_id = vct00) %>% 
  spread(., key = c("descr"), value = "val") %>% 
  dplyr::select(., run_id, no_del, dens, sum_newip, sum_trltls, ticks)
# saving wide format observations
data01 %>% 
   saveRDS(., file = "./RawData/nw_sim_ban_noip10_ls7_356_wide_01.RDS")

## First Plot of Results "Warning"
# with all observations (including those stopping before 365 days)
data02 <- data01 %>%
          group_by(no_del, dens) %>% 
          summarize(mn_newip = mean(sum_newip), sd_newip = sd(sum_newip))
# only observatons that ran to 365 days
data03 <- data01 %>%
          filter(., ticks == 365) %>% 
          group_by(no_del, dens) %>% 
          summarize(mn_newip = mean(sum_newip), sd_newip = sd(sum_newip))
```
<br>


##### 3.2 Descriptive and OLS

```{r 03_02 ban_OLS, include = TRUE, results = TRUE, eval = TRUE, message = FALSE, warning = FALSE}

## Numbers of ticks for all rounds
# calculating
res_d00 <- data01 %>% 
  group_by(., no_del, dens) %>% 
  summarize(mean = mean(ticks))
# showing
res_d00

#### performing OLS ----------------------------------------------

## for network density "real" ----------
# all observations
res01a <- data01 %>% 
         filter(., dens %in% "real") %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res01a)

# observations that ran for 365 days
res01b <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "real") %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res01b)

# observations that ran for 365 days & between point 0 & 1
res01b_0_1 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "real") %>%
         filter(., no_del == 0 | no_del == 91) %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res01b_0_1)

# observations that ran for 365 days & between point 1 & 2
res01b_1_2 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "real") %>%
         filter(., no_del == 91 | no_del == 183) %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res01b_1_2)

# observations that ran for 365 days & between point 2 & 3
res01b_2_3 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "real") %>%
         filter(., no_del == 183 | no_del == 273) %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res01b_2_3)

# # observations that ran for 365 days & between point 0 & 2
res01b_0_3 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "real") %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res01b_0_3)


## for network density "sim_15" ----------
# all observations
res02a <- data01 %>% 
         filter(., dens %in% "sim_15") %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res02a)

# observations that ran for 365 days
res02b <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_15") %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res02b)

# observations that ran for 365 days & between point 0 & 1
res02b_0_1 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_15") %>%
         filter(., no_del == 0 | no_del == 91) %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res02b_0_1)

# observations that ran for 365 days & between point 1 & 2
res02b_1_2 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_15") %>%
         filter(., no_del == 91 | no_del == 183) %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res02b_1_2)

# observations that ran for 365 days & between point 0 & 2
res02b_0_2 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_15") %>%
         lm(data = ., formula = sum_newip ~ no_del)
summary(res02b_0_2)


## for network density "sim_30" ----------
# all observations
res03a <- data01 %>% 
         filter(., dens %in% "sim_30") %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res03a)

# observations that ran for 365 days
res03b <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_30") %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res03b)

# observations that ran for 365 days & between point 0 & 1
res03b_0_1 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_30") %>%
         filter(., no_del == 0 | no_del == 91) %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res03b_0_1)

# observations that ran for 365 days & between point 1 & 2
res03b_1_2 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_30") %>%
         filter(., no_del == 91 | no_del == 183) %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res03b_1_2)

# # observations that ran for 365 days & between point 2 & 3
res03b_2_3 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_30") %>% 
         filter(., no_del == 183 | no_del == 273) %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res03b_2_3)

# observations that ran for 365 days & between point 0 & 3
res03b_0_3 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_30") %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res03b_0_3)

## for network density "sim_45" ----------
# all observations
res04a <- data01 %>% 
         filter(., dens %in% "sim_45") %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res04a)

# observations that ran for 365 days
res04b <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_45") %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res04b)

# observations that ran for 365 days & between point 0 & 1
res04b_0_1 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_45") %>%
         filter(., no_del == 0 | no_del == 91) %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res04b_0_1)

# observations that ran for 365 days & between point 1 & 2
res04b_1_2 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_45") %>%
         filter(., no_del == 91 | no_del == 183) %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res04b_1_2)

# observations that ran for 365 days & between point 2 & 3
res04b_2_3 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_45") %>%
         filter(., no_del == 183 | no_del == 273) %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res04b_2_3)

# observations that ran for 365 days & between point 0 & 3
res04b_0_3 <- data01 %>% 
         filter(., ticks == 365) %>% 
         filter(., dens %in% "sim_45") %>% 
         lm(data = ., formula = sum_newip ~ no_del)
summary(res04b_0_3)


#### saving results
## "real", observations that ran 365 days
# defining column labels
col_lab = c("0 to 91", "91 to 183",
            "183 to 273", "0 to 273")
# rendering and saving regression table
stargazer(res01b_0_1, res01b_1_2,
          res01b_2_3, res01b_0_3,
         column.labels = col_lab,
         title = "Countermeasure Account Ban",
         style = "apsr",
         digits = 2,
         type = "html",
         out = "./PlotsTables/ols_ban_noip10_lstwt07_365_real_02.html")

## All models, observations that ran 365 days
# defining column labels
col_lab = c("Sim 15: 0-91", "Sim 15: 91-183", "Sim 15: 0-183",
            "Sim 30: 0-91", "Sim 30: 91-183", "Sim 30: 183-273", "Sim 30: 0-273",
            "Sim 45: 0-91", "Sim 45: 91-183", "Sim 45: 183-273", "Sim 45: 0-273",
            "Real: 0-91", "Real: 91-183", "Real: 183-273", "Real: 0-273")
# rendering and saving regression table
stargazer(res02b_0_1, res02b_1_2, res02b_0_2,
          res03b_0_1, res03b_1_2, res03b_2_3, res03b_0_3,
          res04b_0_1, res04b_1_2, res04b_2_3, res04b_0_3,
          res01b_0_1, res01b_1_2, res01b_2_3, res01b_0_3,
          column.labels = col_lab,
          title = "Countermeasure Account Ban",
          style = "apsr",
          digits = 2,
          type = "html",
          out = "./PlotsTables/ols_ban_noip10_lstwt07_365_sim_02.html")

# Getting Summary of 183 banned accounts
res05 <- data01 %>% 
         filter(., dens %in% "real") %>% 
         filter(., no_del == 0 ) %>% 
        # dplyr::select(., ticks) %>% 
         summary(.)
res05

# Getting Number of runs with less than 365 days runtime
res06 <- data01 %>% 
         filter(., dens %in% "real") %>% 
         filter(., no_del == 0) %>% 
         arrange(desc(ticks))
res06


###### Doing Hypotheses Tests for [H2b] ----------------------------------------------

#### For Real-World Network
# for portion 0 accounts to 91 accounts
int_res01b_0_1 <- res01b_0_1 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res01b_0_1 <-  int_res01b_0_1[2, "Estimate"]
se_res01b_0_1 <- int_res01b_0_1[2, "Std. Error"]

# for portion 91 accounts to 183 accounts
int_res01b_1_2 <- res01b_1_2 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res01b_1_2 <-  int_res01b_1_2[2, "Estimate"]
se_res01b_1_2 <- int_res01b_1_2[2, "Std. Error"]

# for portion 183 accounts to 273 accounts
int_res01b_2_3 <- res01b_2_3 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res01b_2_3 <-  int_res01b_2_3[2, "Estimate"]
se_res01b_2_3 <- int_res01b_2_3[2, "Std. Error"]

# calculation Z-Value & getting p-value
# portion 0 to 183 accounts
z_res01b_0_2 <- (b_res01b_1_2 - b_res01b_0_1)/sqrt( (se_res01b_1_2)^2 + (se_res01b_0_1)^2 ) 
p_res01b_0_2 <- pnorm(q = z_res01b_0_2, lower.tail = TRUE)
p_res01b_0_2 

# portion 91 to 273 accounts
z_res01b_1_3 <- (b_res01b_2_3 - b_res01b_1_2)/sqrt( (se_res01b_2_3)^2 + (se_res01b_1_2)^2 ) 
p_res01b_1_3 <- pnorm(q = z_res01b_1_3, lower.tail = TRUE)
p_res01b_1_3 

#### For 15 artificial Network
# for portion 0 accounts to 91 accounts
int_res02b_0_1 <- res02b_0_1 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res02b_0_1 <-  int_res02b_0_1[2, "Estimate"]
se_res02b_0_1 <- int_res02b_0_1[2, "Std. Error"]

# for portion 91 accounts to 183 accounts
int_res02b_1_2 <- res02b_1_2 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res02b_1_2 <-  int_res02b_1_2[2, "Estimate"]
se_res02b_1_2 <- int_res02b_1_2[2, "Std. Error"]

# calculation Z-Value & getting p-value
# portion 0 to 183 accounts
z_res02b_0_2 <- (b_res02b_1_2 - b_res02b_0_1)/sqrt( (se_res02b_1_2)^2 + (se_res02b_0_1)^2 ) 
p_res02b_0_2 <- pnorm(q = z_res02b_0_2, lower.tail = TRUE)
p_res02b_0_2 


#### For 30 artificial Network
# for portion 0 accounts to 91 accounts
int_res03b_0_1 <- res03b_0_1 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res03b_0_1 <-  int_res03b_0_1[2, "Estimate"]
se_res03b_0_1 <- int_res03b_0_1[2, "Std. Error"]

# for portion 91 accounts to 183 accounts
int_res03b_1_2 <- res03b_1_2 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res03b_1_2 <-  int_res03b_1_2[2, "Estimate"]
se_res03b_1_2 <- int_res03b_1_2[2, "Std. Error"]

# for portion 183 accounts to 273 accounts
int_res03b_2_3 <- res03b_2_3 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res03b_2_3 <-  int_res03b_2_3[2, "Estimate"]
se_res03b_2_3 <- int_res03b_2_3[2, "Std. Error"]

# calculation Z-Value & getting p-value
# portion 0 to 183 accounts
z_res03b_0_2 <- (b_res03b_1_2 - b_res03b_0_1)/sqrt( (se_res03b_1_2)^2 + (se_res03b_0_1)^2 ) 
p_res03b_0_2 <- pnorm(q = z_res03b_0_2, lower.tail = TRUE)
p_res03b_0_2 

# portion 91 to 273 accounts
z_res03b_1_3 <- (b_res03b_2_3 - b_res03b_1_2)/sqrt( (se_res03b_2_3)^2 + (se_res03b_1_2)^2 ) 
p_res03b_1_3 <- pnorm(q = z_res03b_1_3, lower.tail = TRUE)
p_res03b_1_3 


#### For 45 artificial Network
# for portion 0 accounts to 91 accounts
int_res04b_0_1 <- res04b_0_1 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res04b_0_1 <-  int_res04b_0_1[2, "Estimate"]
se_res04b_0_1 <- int_res04b_0_1[2, "Std. Error"]

# for portion 91 accounts to 183 accounts
int_res04b_1_2 <- res04b_1_2 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res04b_1_2 <-  int_res04b_1_2[2, "Estimate"]
se_res04b_1_2 <- int_res04b_1_2[2, "Std. Error"]

# for portion 183 accounts to 273 accounts
int_res04b_2_3 <- res04b_2_3 %>% 
  summary(.) %>%
  coef(.) %>% 
  as.data.frame(.) %>% 
  dplyr::select(., Estimate, "Std. Error")
# getting coefficient ("b") and standard error ("se")
b_res04b_2_3 <-  int_res04b_2_3[2, "Estimate"]
se_res04b_2_3 <- int_res04b_2_3[2, "Std. Error"]

# calculation Z-Value & getting p-value
# portion 0 to 183 accounts
z_res04b_0_2 <- (b_res04b_1_2 - b_res04b_0_1)/sqrt( (se_res04b_1_2)^2 + (se_res04b_0_1)^2 ) 
p_res04b_0_2 <- pnorm(q = z_res04b_0_2, lower.tail = TRUE)
p_res04b_0_2 

# portion 91 to 273 accounts
z_res04b_1_3 <- (b_res04b_2_3 - b_res04b_1_2)/sqrt( (se_res04b_2_3)^2 + (se_res04b_1_2)^2 ) 
p_res04b_1_3 <- pnorm(q = z_res04b_1_3, lower.tail = TRUE)
p_res04b_1_3 


h_test00 <- data.frame(Network = c("Real-World: Diff. Effect",
                                 "Real-World: p-Value",
                                 
                                 "Art. 15: Diff. Effect",
                                 "Art. 15: p-Value",
                                 
                                 "Art. 30: Diff. Effect",
                                 "Art. 30: p-Value",
                                 
                                 "Art. 45: Diff. Effect",
                                 "Art. 45: p-Value"),
                     
                     "0 acc. - 91 acc. vs. 91 acc. - 183 acc." = c((b_res01b_1_2 - b_res01b_0_1), # real-world
                                                p_res01b_0_2,
                                                
                                                c((b_res02b_1_2 - b_res02b_0_1), # real-world
                                                p_res02b_0_2,
                                                
                                                (b_res03b_1_2 - b_res03b_0_1),   # artificial 30
                                                p_res03b_0_2,
                                                  
                                                (b_res04b_1_2 - b_res04b_0_1),   # artificial 45
                                                p_res04b_0_2)),
                     
                     
                     "91 acc. - 183 acc. vs. 183 acc. - 273 acc." = c((b_res01b_2_3 - b_res01b_1_2), # real-world
                                                p_res01b_1_3,
                     
                                                 NA,   # artificial 15
                                                 NA,
                                                 
                                                (b_res03b_2_3 - b_res03b_1_2),   # artificial 30
                                                p_res03b_1_3,
                                                 
                                                (b_res04b_2_3 - b_res04b_1_2),   # artificial 45
                                                p_res04b_1_3)) %>% 
  
  `colnames<-`(c("Network",
                 "0 acc. - 91 acc. vs. 91 acc. - 183 acc.",
                 "91 acc. - 183 acc. vs. 183 acc. - 273 acc."))

# displaying hypothesis test table
h_test00 %>% kable(.)


####### Doing Hypotheses Tests for [H3] ----------------------------------------------
## NOTE: I take advantage that coeficients and standard errors are already defined

## Art. 15 vs. Art. 30
# Portion 0 acc. to 91 acc.
z_res0203_0_1 <- (b_res02b_0_1 - b_res03b_0_1)/sqrt( (se_res02b_0_1)^2 + (se_res03b_0_1)^2 ) 
p_res0203_0_1 <- pnorm(q = z_res0203_0_1, lower.tail = TRUE)
p_res0203_0_1

# Portion 91 acc. to 183 acc.
z_res0203_1_2 <- (b_res02b_1_2 - b_res03b_1_2)/sqrt( (se_res02b_1_2)^2 + (se_res03b_1_2)^2 ) 
p_res0203_1_2 <- pnorm(q = z_res0203_1_2, lower.tail = TRUE)
p_res0203_1_2

# Portion 183 acc. to 273 acc.
# NA


## Art. 30 vs. Art. 45
# Portion 0 acc. to 91 acc.
z_res0304_0_1 <- (b_res03b_0_1 - b_res04b_0_1)/sqrt( (se_res03b_0_1)^2 + (se_res04b_0_1)^2 ) 
p_res0304_0_1 <- pnorm(q = z_res0304_0_1, lower.tail = TRUE)
p_res0304_0_1

# Portion 91 acc. to 183 acc.
z_res0304_1_2 <- (b_res03b_1_2 - b_res04b_1_2)/sqrt( (se_res03b_1_2)^2 + (se_res04b_1_2)^2 ) 
p_res0304_1_2 <- pnorm(q = z_res0304_1_2, lower.tail = TRUE)
p_res0304_1_2

# Portion 183 acc. to 273 acc.
z_res0304_2_3 <- (b_res03b_2_3 - b_res04b_2_3)/sqrt( (se_res03b_2_3)^2 + (se_res04b_2_3)^2 ) 
p_res0304_2_3 <- pnorm(q = z_res0304_2_3, lower.tail = TRUE)
p_res0304_2_3


## preparing and displaying result data frame
# preparing result data frame
h_test01 <- data.frame(Network = c("0 acc. - 91 acc.: Diff. Effect",
                                   "0 acc. - 91 acc.: p-Value",

                                   "91 acc. - 183 acc.: Diff. Effect",
                                   "91 acc. - 183 acc.: p-Value",

                                   "183 acc. - 273 acc.: Diff. Effect",
                                   "183 acc. - 273 acc.: p-Value"),

                     "Art. 15 vs. Art. 30" = c((b_res03b_0_1 - b_res02b_0_1), 
                                                p_res0203_0_1,

                                              c(b_res03b_1_2 - b_res02b_1_2), 
                                                p_res0203_1_2,
                                               
                                                NA,
                                                NA),


                     "Art. 30 vs. Art. 45"     = c((b_res04b_0_1 - b_res03b_0_1),
                                                 p_res0304_0_1,

                                                 c(b_res04b_1_2 - b_res03b_1_2),  
                                                 p_res0304_1_2,

                                                 c(b_res04b_2_3 - b_res03b_2_3),  
                                                 p_res0304_2_3)) %>% 
  
`colnames<-`(c("Network", "Art. 15 vs. Art. 30", "Art. 30 vs. Art. 45"))

# displaying result data frame
h_test01%>% kable(.)


```
<br>

##### 3.3 Plots

```{r 03_01 ban_plots, include = TRUE, results = TRUE, eval = TRUE, message = FALSE, warning = FALSE}


##### creating plots -----------------------------------------------------------------
## "Real-Life" Network Only
# Preparing Data
data04 <- data02 %>% 
  filter(., dens %in% "real") %>% 
  filter(., no_del >= 183) %>% 
  mutate(., dat_bas = "all")
data05 <- data03 %>% 
  filter(., dens %in% "real") %>% 
  mutate(., dat_bas = "365_oly")
data06 <- data04 %>% 
  rbind(., data05)

# rendering, showing and saving plot
gg01 <- data06 %>%
        ggplot( aes(x = no_del, 
                    group = dat_bas,
                    color = dat_bas) ) +
  
        geom_line(aes(y = mn_newip ) ) +
  
        geom_errorbar(aes(ymin = mn_newip - sd_newip,
                          ymax = mn_newip + sd_newip),
                      colour = "black",
                      width = 5.0,
                      size = 0.5) +
  
        geom_point(aes(y = mn_newip),
                       size = 1.5) +

        scale_y_continuous(name ="Information Pollution Tweets [-]",
                           limits = c(-50, 3550)) +
  
        scale_x_continuous(name = "Accounts Banned [-]",
                           breaks = c(0, 91, 183, 273),
                           limits = c(-1, 274)) +
  
        scale_color_grey(name = "Runs:",
                         labels = c("365 days", "Less than\n365 days")) +

        theme_bw()

# saving plot
gg01 %>% 
  ggsave(., filename = "./PlotsTables/plt_ban_noip10_lstwt07_real_allobs_01.png",
      units = "cm",
      dpi = "retina",
      height = 8,
      width = 14)


#### "Artificial Network" 365 days Only ---------------------------------------
# rendering
gg02 <- data03 %>%
  
        filter(., dens %in% c("sim_15", "sim_30", "sim_45")) %>%  
  
        ggplot( aes(x = no_del,
                    group = dens,
                    color = dens) ) +
  
        geom_line(aes(y = mn_newip ),
                      size = 1.0) +
  
        geom_errorbar(aes(ymin = mn_newip - sd_newip,
                          ymax = mn_newip + sd_newip),
                          colour = "black",
                          width = 3.5,
                          size = 0.5) +
  
        geom_point(aes(y = mn_newip),
                       size = 1.5) +

        scale_y_continuous(name ="Information Pollution Tweets [--]",
                           limits = c(-50, 5100)) +

        scale_x_continuous(name = "Accounts Banned [-]",
                           breaks = c(0, 91, 183, 273),
                           limits = c(-1, 274)) +
  
        scale_color_grey(name = "Density:",
                         labels = c("15 links", "30 links", "45 links")) +

        theme_bw()

# showing plot
gg02
# saving plot
gg02 %>% 
  ggsave(., filename = "./PlotsTables/plt_ban_noip10_lstwt07_artif_365_01.png",
      units = "cm",
      dpi = "retina",
      height = 8,
      width = 14)


#### Real and Artificial Networks, All Observations ---------------------------------------
# rendering
gg03 <- data02 %>%
  
        ggplot( aes(x = no_del,
                    group = dens,
                    color = dens) ) +
  
        geom_line(aes(y = mn_newip ),
                      size = 1.0) +
  
        geom_errorbar(aes(ymin = mn_newip - sd_newip,
                          ymax = mn_newip + sd_newip),
                          colour = "black",
                          width = 2.0,
                          size = 0.5) +
  
        geom_point(aes(y = mn_newip),
                       size = 1.5) +

        scale_y_continuous(name ="Information Pollution Tweets [--]",
                           limits = c(-50, 5100)) +

        scale_x_continuous(name = "Accounts Banned [-]",
                           breaks = c(0, 91, 183, 273),
                           limits = c(-1, 274)) +
  
        scale_color_grey(name = "Network:",
                         labels = c("Real 30", "Artif. 15", "Artif. 30", "Artif. 45")) +

        theme_bw()

# showing plot
gg03

# saving plot
gg03 %>% 
  ggsave(., filename = "./PlotsTables/plt_ban_noip10_lstwt07_all_allobs_01.png",
      units = "cm",
      dpi = "retina",
      height = 8,
      width = 14)


## removing auxillary variables
rm(col_lab, n_row)
rm(list= ls(pattern= "data"))
rm(list= ls(pattern= "vct"))
rm(list= ls(pattern= "res"))
rm(list= ls(pattern= "gg"))
```

