---
title: "MT **Scraping**  05"
author: "Markus Rottmann"
date: "2021 01 23"
output:
  html_document:
      toc: true
      toc_depth: 5
---


```{r setup, include = TRUE, warning = FALSE, message = FALSE, eval = FALSE}

## 0.1: clearing memory
rm(list=ls(all=T))

## 0.2 defining options
options(repos = "https://cran.rstudio.com")
options(stringsAsFactors = FALSE)
knitr::opts_chunk$set(echo = TRUE, fig.width = 7, fig.height = 5)


## 0.3 loading (and installing) packages
# defining required packages
req_packages <- c("dplyr", "knitr", "kableExtra", "rvest", "igraph",
"ggplot2", "tibble", "quanteda", "stargazer", "tidyr", "stringr", "lme4",
"rtweet", "lubridate")

# checking, if already installed
new_packages <- req_packages[!(req_packages %in% installed.packages()[,"Package"])]

# installing (downloading) missing packages
if(length(new_packages) > 0) {
  install.packages(new_packages)
} 

# loading required packages
lapply(req_packages, library, character.only = TRUE) 

# removing auxillary variabels
rm(req_packages, new_packages) 

# frequenty needed packages: ("dplyr", "knitr", "kableExtra", "rvest", "igraph",
# "pageviews", "WikipediR", "ggplot2", "tibble", "quanteda", "stargazer", "tidyr",
# "stringr", "lme4", "rtweet", "lubridate")



```

&nbsp;

***

### Description

  + This Code Scrapes the Tweets of all candidates for 2019 elections and combines it into a data frame that also contains properties such as gender, age, party, etc. 
  + For the sake of privacy, all twitter API information is set to "YYY".
  + All code chunks are set `eval = FALSE` due to the very long running time of this code.


&nbsp;

***


### 1. Generating Source List with Twitter-Adresses of all Candidates for Elections 2019

**Description:** Generating source list containing all candidates for 2019 elections (National Council and Council of States)


**Data:**

 * input: `2019_chvote_nationalcouncil.csv`, `2019_chvote_councilofstates.csv`
 * output: `df_tweets_all_00.rds`


```{r 01, include = TRUE, results = TRUE, eval = FALSE, message = FALSE, warning = FALSE}

### Loading & Preparing Base Data Sets
## Data Set: National Council
var_sel_nc <- c("firstname", "lastname", "party_short", "gender", "year_of_birth", "zip", "city", "district", "list", "list_place_1",      "LINK_personal_website", "LINK_facebook", "LINK_Twitter", "LINK_Instagram", "incumbent") # defining variables

data_nc <- read.csv("./RawData/2019_chvote_nationalcouncil.csv", encoding = "UTF-8") %>% 
  select(., var_sel_nc) # reading-in data and selecting defined variables

data_nc$nc <- as.factor(1) # dummy variable indicating candidateship
data_nc$sc <- as.factor(0) # dummy variable indicating candidateship

## Data Set: Council of states
var_sel_sc <- c("X.U.FEFF.firstname", "lastname", "party_short", "gender", "year_of_birth", "zip", "city", "district", "LINK_personal_website", "LINK_facebook", "LINK_Twitter", "LINK_Instagram", "incumbent") # defining variables

data_sc <- read.csv("./RawData/2019_chvote_councilofstates.csv", encoding = "UTF-8") %>% 
  select(., var_sel_sc) # reading-in data and selecting defined variables

data_sc$list <- as.character(NA) # adding (missing) variable (list not applicalbe for counc. o. states)
data_sc$list_place_1 <- as.character(NA) # adding (missing) variable (list not applicalbe for counc. o. states)

data_sc$nc <- as.factor(0) # dummy variable indicating candidateship
data_sc$sc <- as.factor(1) # dummy variable indicating candidateship

names(data_sc)[names(data_sc) == "X.U.FEFF.firstname"] <- "firstname" # harmonizing firstname variable


### Binding both data sets and assigning an unique ID "id" to all observations (rows)
data00 <- base::rbind(data_nc, data_sc)
data00$id <- as.numeric(1:nrow(data00))

### Saving source List and deleting intermediate variables
saveRDS(data00, file = "./DataFrames/df_source_all_00.rds")
rm(var_sel_nc, var_sel_sc, data_nc, data_sc)
rm(data00)

```



&nbsp;

***


### 2. Tweet Scraping (Tweet Gathering)
<br>

#### 2.1 Preparation

**Description:** Authentificating Twitter API.

**NOTE:**

 - `eval = FALSE` because of long download times


```{r 02_01, include = TRUE, results = TRUE, eval = FALSE, message = FALSE, warning = FALSE}

#### authentificating twitter api
token <- create_token(app = "master_thesis",
consumer_key = "YYY",
consumer_secret =
"YYY",
access_token = "YYY",
access_secret = "YYY")


```
<br>

#### 2.2 Tweet Scrape

**Description:**

1. Filtering those candidates that have a Twitter-Account
2. Scraping last 3'200 Tweets of all candidates with Twitter-Account

<br>

**Data:**

 * input: `df_source_all_00.rds`
 * output: `df_tweets_all.rds`

<br>

**NOTE:**

 - `eval = FALSE` because of long download times
 - this had to be done a few times, for Twitter's IPA has a rate limit.
   - df_tweets_all_01.rds: up to id = 142
   - df_tweets_all_02.rds: from id = 143 up to id = 823
   - df_tweets_all_03.rds: from id = 824 up to id = 
   - df_tweets_all_04.rds: from id = up to id =
   - df_tweets_all_05.rds: from id = up to id = 3626
   - df_tweets_all_06.rds: from id = 3627 up to id = 3806
   - df_tweets_all_07.rds: from id = 3807 up to id =


```{r 02_02, include = TRUE, results = TRUE, eval = FALSE, message = FALSE, warning = FALSE}

#### Reading-in source list & filtering candidates with Twitter account
data02 <- readRDS(file = "./DataFrames/df_source_all_00.rds") %>% 
    filter(., !(LINK_Twitter %in% NA))


#### Scraping last 3'200 Tweets in Loop
# filtering base data list down, due to restrictions wrt. Twitters maximum of downloads
data03 <- data02 %>% 
  filter(., id >= 3807)

# creating support data frame
df_help0 <- rep(NA, 99) # creating support data frame

# actual scraping loop
for (i in 1:nrow(data03)) try({
  df_help <- data03[i, "LINK_Twitter"] %>% 
  sub(".*https://twitter.com/", "", .) %>% 
  get_timeline(., n = 3200)
  
  df_help$lastname <- data03[i, "lastname"]
  df_help$firstname <- data03[i, "firstname"]
  df_help$party_short <- data03[i, "party_short"]
  df_help$status <- data03[i, "status"]
  df_help$year_of_birth <- data03[i, "year_of_birth"]
  df_help$district <- data03[i, "district"] 
  df_help$zip <- data03[i, "zip"]
  df_help$gender <- data03[i, "gender"]
  df_help$nc <- data03[i, "nc"]
  df_help$sc <- data03[i, "sc"]
  df_help$incumbent <- data03[i, "incumbent"]
  df_help$id <- data03[i, "id"]
  
  df_help0 <- rbind(df_help0, df_help)
  
})

# saving results
df_tweets <- df_help0
saveRDS(df_tweets, file = "./DataFrames/df_tweets_all_07.rds")

# removing intermediate variables
rm(df_help, df_tweets, data02, data03, df_help0, i)


#### Binding all partial downloads
# Reading-in
df_tweets_all_01 <- readRDS("./DataFrames/df_tweets_all_01.rds")
df_tweets_all_02 <- readRDS("./DataFrames/df_tweets_all_02.rds")
df_tweets_all_03 <- readRDS("./DataFrames/df_tweets_all_03.rds")
df_tweets_all_04 <- readRDS("./DataFrames/df_tweets_all_04.rds")
df_tweets_all_05 <- readRDS("./DataFrames/df_tweets_all_05.rds")
df_tweets_all_06 <- readRDS("./DataFrames/df_tweets_all_06.rds")
df_tweets_all_07 <- readRDS("./DataFrames/df_tweets_all_07.rds")

# Binding
df_tweets_all <- rbind(df_tweets_all_01, df_tweets_all_02)
df_tweets_all <- rbind(df_tweets_all, df_tweets_all_03)
df_tweets_all <- rbind(df_tweets_all, df_tweets_all_04)
df_tweets_all <- rbind(df_tweets_all, df_tweets_all_05)
df_tweets_all <- rbind(df_tweets_all, df_tweets_all_06)
df_tweets_all <- rbind(df_tweets_all, df_tweets_all_07)

# saving results
saveRDS(df_tweets_all, file = "./DataFrames/df_tweets_all.rds")

# removing intermediate data
rm(df_tweets_all_01, df_tweets_all_02, df_tweets_all_03,
   df_tweets_all_04, df_tweets_all_05, df_tweets_all_06,
   df_tweets_all_07, df_tweets_all)

```


&nbsp;

***

### 3. Checking for Completeness (all candidates cought?), Manually Rectifying & Scraping

<br>

#### 3.1 Missed tweets because of faulty first portion of link `https://www.twitter...` instead of `https://twitter...`

**Description:** Some tweets were not caught because of a different pattern of twitter links in the source-list.

**NOTE:**

 - `eval = FALSE` to prevent doublification

```{r 03_01, include = TRUE, results = TRUE, eval = FALSE, message = FALSE, warning = FALSE}

# loading source list
data04 <- readRDS(file = "./DataFrames/df_source_all_00.rds") %>% 
    filter(., !(LINK_Twitter %in% NA))

# loading entire corpus
data05 <- readRDS(file = "./DataFrames/df_tweets_all.rds")

# getting a list with *missed* ids
lst_missed_base_01 <- setdiff(x = data04$id, y = data05$id) # identifying missed ids
df_missed_01 <- data04 %>% 
  filter(., id %in% lst_missed_base_01)

# creating support data frame
df_help0 <- rep(NA, 99) # creating support data frame

# actual scraping loop
for (i in 1:nrow(df_missed_01)) try({
  df_help <- df_missed_01[i, "LINK_Twitter"] %>% 
  sub(".*twitter.com/", "", .) %>% 
  get_timeline(., n = 3200)
  
  df_help$lastname <- df_missed_01[i, "lastname"]
  df_help$firstname <- df_missed_01[i, "firstname"]
  df_help$party_short <- df_missed_01[i, "party_short"]
  df_help$status <- df_missed_01[i, "status"]
  df_help$year_of_birth <- df_missed_01[i, "year_of_birth"]
  df_help$district <- df_missed_01[i, "district"] 
  df_help$zip <- df_missed_01[i, "zip"]
  df_help$gender <- df_missed_01[i, "gender"]
  df_help$nc <- df_missed_01[i, "nc"]
  df_help$sc <- df_missed_01[i, "sc"]
  df_help$incumbent <- df_missed_01[i, "incumbent"]
  df_help$id <- df_missed_01[i, "id"]
  
  df_help0 <- rbind(df_help0, df_help)
  
})

# saving results
df_tweets <- df_help0
saveRDS(df_tweets, file = "./DataFrames/df_tweets_missed_01.rds")

# merging second retreived 
df_tweets_all <- readRDS(file = "./DataFrames/df_tweets_all.rds")
df_tweets_missed_01 <- readRDS(file = "./DataFrames/df_tweets_missed_01.rds")
df_tweets_all <- rbind(df_tweets_all, df_tweets_missed_01)

#saving
saveRDS(df_tweets_all, file = "./DataFrames/df_tweets_all.rds")


# deleting intermediate variables
rm(i, df_help, df_help0, lst_missed_base_01, df_tweets_missed_01, df_tweets_all, data04, data05, df_tweets)

```
<br>

#### 3.2 Missed tweets because of faulty last portion of link (e.g. wrongly spelled names)


**Description:** Some tweets are not caught because of faulty last portion of the twitter link in the source list.

1. Rectifying Language Extension (e.g. "?lang=de") and Unknown Extension (e.g. "?c2...")
2. Rectifying Other Faulty Links
3. Rectifying/Checking accounts that did not tweet for a long time or are deleted


**NOTE:**

 - `eval = FALSE` to prevent doublification

```{r 03_02, include = TRUE, results = TRUE, eval = FALSE, message = FALSE, warning = FALSE}

######## 1. Rectifying Language Extension (e.g. "?lang=de") and Unknown Extension (e.g. "?c2...")
# loading source list
data06 <- readRDS(file = "./DataFrames/df_source_all_00.rds") %>% 
    filter(., !(LINK_Twitter %in% NA))

# loading entire corpus
data07 <- readRDS(file = "./DataFrames/df_tweets_all.rds")

# getting a df with *missed* ids
lst_missed_base_02 <- setdiff(x = data06$id, y = data07$id) # identifying missed ids
df_missed_02 <- data06 %>% 
  filter(., id %in% lst_missed_base_02)

# making a special dataframe for better scrutiny
twitter <- rep(NA, 500)
id <- rep(as.numeric(NA), 500)
df_help <- cbind.data.frame(twitter, id)

# getting rid of first portion of "LINK_Twitter"
for (i in 1:nrow(df_missed_02)) try({
  df_help[i, "twitter"] <- df_missed_02[i, "LINK_Twitter"] %>% 
  sub(".*twitter.com/", "", .)
  df_help[i, "id"] <- df_missed_02[i, "id"]
})

# getting rid of language indicator (does not work with "get_timeline()")
df_help$twitter_cleaned <- sub(pattern = "?lang=de", "", df_help$twitter, fixed = TRUE)
df_help$twitter_cleaned <- sub(pattern = "?lang=fr", "", df_help$twitter_cleaned, fixed = TRUE)
df_help$twitter_cleaned <- sub(pattern = "?lang=en", "", df_help$twitter_cleaned, fixed = TRUE)
df_help$twitter_cleaned <- sub(pattern = "?lang=ar", "", df_help$twitter_cleaned, fixed = TRUE)

# manually rectifying faulty entries in source list, part 1
df_help[which(df_help$id == 39), "twitter_cleaned"] <- "MichaelSchibli"
df_help[which(df_help$id == 121), "twitter_cleaned"] <- "HarryLutolf"
df_help[which(df_help$id == 176), "twitter_cleaned"] <-"_MMMXI_"
df_help[which(df_help$id == 564), "twitter_cleaned"] <- "MelvinImhof"
df_help[which(df_help$id == 1880), "twitter_cleaned"] <- "priskahafner"
df_help[which(df_help$id == 2907), "twitter_cleaned"] <- "Fior000"
df_help[which(df_help$id == 2986), "twitter_cleaned"] <- "DAngeloVladimir"
df_help[which(df_help$id == 2999), "twitter_cleaned"] <- "CantoneFabienne"
df_help[which(df_help$id == 3000), "twitter_cleaned"] <- "CamilleCantone"
df_help[which(df_help$id == 3012), "twitter_cleaned"] <- "AnaBerclaz"
df_help[which(df_help$id == 3651), "twitter_cleaned"] <- "NinaFehrDuesel"
df_help[which(df_help$id == 4574), "twitter_cleaned"] <- "EAugstburger"

# merging cleaned twitter name with missing df
df_missed_02 <- merge(x = df_missed_02, y = df_help, by = "id")
rm(df_help)

# creating support data frame
df_help0 <- rep(NA, 99) # creating support data frame

# scraping missing tweets
for (i in 1:nrow(df_missed_02)) try({
  df_help <- df_missed_02[i, "twitter_cleaned"] %>% 
  get_timeline(., n = 3200)
  
  df_help$lastname <- df_missed_02[i, "lastname"]
  df_help$firstname <- df_missed_02[i, "firstname"]
  df_help$party_short <- df_missed_02[i, "party_short"]
  df_help$status <- df_missed_02[i, "status"]
  df_help$year_of_birth <- df_missed_02[i, "year_of_birth"]
  df_help$district <- df_missed_02[i, "district"] 
  df_help$zip <- df_missed_02[i, "zip"]
  df_help$gender <- df_missed_02[i, "gender"]
  df_help$nc <- df_missed_02[i, "nc"]
  df_help$sc <- df_missed_02[i, "sc"]
  df_help$incumbent <- df_missed_02[i, "incumbent"]
  df_help$id <- df_missed_02[i, "id"]
  
  df_help0 <- rbind(df_help0, df_help)
  
})

# saving results
df_tweets <- df_help0
saveRDS(df_tweets, file = "./DataFrames/df_tweets_missed_02.rds")

# merging third retreived and save
df_tweets_all <- readRDS(file = "./DataFrames/df_tweets_all.rds")
df_tweets_missed_02 <- readRDS(file = "./DataFrames/df_tweets_missed_02.rds")
df_tweets_all <- rbind(df_tweets_all, df_tweets_missed_02)
saveRDS(df_tweets_all, file = "./DataFrames/df_tweets_all.rds")

# removing intermediate variables
rm(df_help, df_help0, df_tweets, data06, data07, i, df_tweets_missed_02, lst_missed_base_02)


######## 2. Rectifying Other Faulty Links
data08 <- readRDS(file = "./DataFrames/df_source_all_00.rds") %>% 
    filter(., !(LINK_Twitter %in% NA))

# loading entire corpus & identifying missing ids
data09 <- readRDS(file = "./DataFrames/df_tweets_all.rds")
lst_missed_base_03 <- setdiff(x = data08$id, y = data09$id) # automatically
# manually
lst_missed_base_03a <- c(2907, 2986, 2999, 3000, 3012, 3651, 4574)
twitter_cleaned <- c("Fior000", "DAngeloVladimir", "CantoneFabienne", "CamilleCantone", "AnaBerclaz", "NinaFehrDuesel", "EAugstburger")
df_help_02 <- cbind.data.frame(id = lst_missed_base_03a, twitter_cleaned = twitter_cleaned)

# manufacturing auxillary data frame for better scrutiny
df_help_03 <- data08 %>% 
  filter(., id %in% lst_missed_base_03a)
df_missed_03 <- merge(x = df_help_03, y = df_help_02, by = "id")
rm(df_help)


# scraping missing Links
df_help0 <- rep(NA, 99) # creating support data frame

# actual scraping loop
for (i in 1:nrow(df_missed_03)) try({
  df_help <- df_missed_03[i, "twitter_cleaned"] %>% 
  get_timeline(., n = 3200)
  
  df_help$lastname <- df_missed_03[i, "lastname"]
  df_help$firstname <- df_missed_03[i, "firstname"]
  df_help$party_short <- df_missed_03[i, "party_short"]
  df_help$status <- df_missed_03[i, "status"]
  df_help$year_of_birth <- df_missed_03[i, "year_of_birth"]
  df_help$district <- df_missed_03[i, "district"] 
  df_help$zip <- df_missed_03[i, "zip"]
  df_help$gender <- df_missed_03[i, "gender"]
  df_help$nc <- df_missed_03[i, "nc"]
  df_help$sc <- df_missed_03[i, "sc"]
  df_help$incumbent <- df_missed_03[i, "incumbent"]
  df_help$id <- df_missed_03[i, "id"]
  
  df_help0 <- rbind(df_help0, df_help)
  
})

# saving results
df_tweets <- df_help0
saveRDS(df_tweets, file = "./DataFrames/df_tweets_missed_03.rds")

# merging third retreived and save
df_tweets_all <- readRDS(file = "./DataFrames/df_tweets_all.rds")
df_tweets_missed_03 <- readRDS(file = "./DataFrames/df_tweets_missed_03.rds")
df_tweets_all <- rbind(df_tweets_all, df_tweets_missed_03)
saveRDS(df_tweets_all, file = "./DataFrames/df_tweets_all.rds")

# removing auxillary variables & data frames
rm(data08, data09, i, df_help, df_help0, df_help_02, df_help_03, lst_missed_base_03,
   lst_missed_base_03a, df_tweets, df_missed_03, df_tweets_missed_03, twitter_cleaned, df_tweets_all)



###### 3. Rectifying/Checking accounts that did not tweet for a long time or are deleted
# reading-in source list
data10 <- readRDS(file = "./DataFrames/df_source_all_00.rds") %>% 
    filter(., !(LINK_Twitter %in% NA))

# loading entire corpus & identifying missing ids
data11 <- readRDS(file = "./DataFrames/df_tweets_all.rds")
lst_missed_base_04 <- setdiff(x = data10$id, y = data11$id) # getting list off missing ids

# defining manually elaborated non-existent twitter-ids (all incumbent checkt, rest erratic)
rm_id <- c(24, 42, 58, 60, 61, 74, 75, 84, 85, 102, 112, 123, 145, 541
           , 571, 582, 590, 593, 705, 999, 1580, 1733, 1914, 2420, 3012,
           3585, 4523, 4597)


lst_missed_04 <- setdiff(x = lst_missed_base_04, y = rm_id)


# removing "non-existant", "private only" or "never-tweeted"
df_missed_04 <- data10 %>% 
  filter(., id %in% lst_missed_04)

# manually adjusting twitter handle for incumbent
df_missed_04[which(df_missed_04$id == 167), "LINK_Twitter"] <- "	https://twitter.com/andreas_glarner"
df_missed_04[which(df_missed_04$id == 556), "LINK_Twitter"] <- "	https://twitter.com/mayagraf_bl"
df_missed_04[which(df_missed_04$id == 3665), "LINK_Twitter"] <- "	https://twitter.com/FabianMolinaNR"


# scraping missing Links
df_help0 <- rep(NA, 99) # creating support data frame

# actual scraping loop
for (i in 1:nrow(df_missed_04)) try({
  df_help <- df_missed_04[i, "LINK_Twitter"] %>% 
  sub(".*twitter.com/", "", .) %>% 
  get_timeline(., n = 3200)
  
  df_help$lastname <- df_missed_04[i, "lastname"]
  df_help$firstname <- df_missed_04[i, "firstname"]
  df_help$party_short <- df_missed_04[i, "party_short"]
  df_help$status <- df_missed_04[i, "status"]
  df_help$year_of_birth <- df_missed_04[i, "year_of_birth"]
  df_help$district <- df_missed_04[i, "district"] 
  df_help$zip <- df_missed_04[i, "zip"]
  df_help$gender <- df_missed_04[i, "gender"]
  df_help$nc <- df_missed_04[i, "nc"]
  df_help$sc <- df_missed_04[i, "sc"]
  df_help$incumbent <- df_missed_04[i, "incumbent"]
  df_help$id <- df_missed_04[i, "id"]
  
  df_help0 <- rbind(df_help0, df_help)
  
})

# saving results
df_tweets <- df_help0
saveRDS(df_tweets, file = "./DataFrames/df_tweets_missed_04.rds")

# merging third retreived and save
df_tweets_all <- readRDS(file = "./DataFrames/df_tweets_all.rds")
df_tweets_missed_04 <- readRDS(file = "./DataFrames/df_tweets_missed_04.rds")
df_tweets_all <- rbind(df_tweets_all, df_tweets_missed_04)
saveRDS(df_tweets_all, file = "./DataFrames/df_tweets_all.rds")

# removing auxillary variables & data frames
rm(data10, data11, i, df_help, df_help0, lst_missed_base_04,
   lst_missed_04, df_tweets, df_missed_04, df_tweets_missed_04, df_tweets_all)




############
data12 <- readRDS(file = "./DataFrames/df_source_all_00.rds") %>% 
    filter(., !(LINK_Twitter %in% NA))

# loading entire corpus & identifying missing ids
data13 <- readRDS(file = "./DataFrames/df_tweets_all.rds")
lst_help <- setdiff(x = data12$id, y = data13$id) # automatically

## substracting non-existent twitter ids
# defining manually checked ids
rm_id <- c(24, 42, 58, 60, 61, 74, 75, 84, 85, 102, 112, 123, 145, 541,
           571, 582, 590, 593, 705, 999, 1580, 1733, 1914, 2420, 3012,
           3585, 4523, 4597)

# elaborating remaining missing
lst_missed_05 <- setdiff(x = lst_help, y = rm_id)

# filtering source list for remaining
df_missed_05 <- data12 %>% 
  filter(., id %in% lst_missed_05) 

# getting rid of language indicator for the second time (does not work with "get_timeline()")
df_missed_05$LINK_Twitter <- sub(pattern = "?lang=de", "", df_missed_05$LINK_Twitter, fixed = TRUE)
df_missed_05$LINK_Twitter <- sub(pattern = "?lang=fr", "", df_missed_05$LINK_Twitter, fixed = TRUE)
df_missed_05$LINK_Twitter <- sub(pattern = "?lang=en", "", df_missed_05$LINK_Twitter, fixed = TRUE)
df_missed_05$LINK_Twitter <- sub(pattern = "?lang=ar", "", df_missed_05$LINK_Twitter, fixed = TRUE)

# renaming twitter handles (due to name change of mistake in source list)
df_missed_05$LINK_Twitter <- sub(pattern = "yvohofer/", "yvohofer", df_missed_05$LINK_Twitter, fixed = TRUE)
df_missed_05$LINK_Twitter <- sub(pattern = "rahel_estermann/", "rahel_estermann", df_missed_05$LINK_Twitter, fixed = TRUE)
df_missed_05$LINK_Twitter <- sub(pattern = "dominiccmueller/", "dominiccmueller", df_missed_05$LINK_Twitter, fixed = TRUE)
df_missed_05$LINK_Twitter <- sub(pattern = "nr_mayagraf", "mayagraf_bl", df_missed_05$LINK_Twitter, fixed = TRUE)

## scraping missing Links
# creating support data frame
df_help0 <- rep(NA, 99)

# looping trough scraping
for (i in 1:nrow(df_missed_05)) try({
  df_help <- df_missed_05[i, "LINK_Twitter"] %>% 
  sub(".*twitter.com/", "", .) %>% 
  get_timeline(., n = 3200)
  
  df_help$lastname <- df_missed_05[i, "lastname"]
  df_help$firstname <- df_missed_05[i, "firstname"]
  df_help$party_short <- df_missed_05[i, "party_short"]
  df_help$status <- df_missed_05[i, "status"]
  df_help$year_of_birth <- df_missed_05[i, "year_of_birth"]
  df_help$district <- df_missed_05[i, "district"] 
  df_help$zip <- df_missed_05[i, "zip"]
  df_help$gender <- df_missed_05[i, "gender"]
  df_help$nc <- df_missed_05[i, "nc"]
  df_help$sc <- df_missed_05[i, "sc"]
  df_help$incumbent <- df_missed_05[i, "incumbent"]
  df_help$id <- df_missed_05[i, "id"]
  
  df_help0 <- rbind(df_help0, df_help)
  
})

# saving results
df_tweets <- df_help0
saveRDS(df_tweets, file = "./DataFrames/df_tweets_missed_05.rds")

# merging third retrieved and save
df_tweets_all <- readRDS(file = "./DataFrames/df_tweets_all.rds")
df_tweets_missed_05 <- readRDS(file = "./DataFrames/df_tweets_missed_05.rds")
df_tweets_all <- rbind(df_tweets_all, df_tweets_missed_05)
saveRDS(df_tweets_all, file = "./DataFrames/df_tweets_all.rds")

# removing auxillary variables
rm(df_help, i, df_help0, df_tweets_all, df_tweets_missed_05, lst_missed_05, df_missed_05_base)







###### 3. Rectifying/Checking accounts that did not tweet for a long time or are deleted
# reading-in source list
data10 <- readRDS(file = "./DataFrames/df_source_all_00.rds") %>% 
    filter(., !(LINK_Twitter %in% NA))

# loading entire corpus & identifying missing ids
data11 <- readRDS(file = "./DataFrames/df_tweets_all.rds")
lst_missed_base_04 <- setdiff(x = data10$id, y = data11$id) # getting list off missing ids


############♣

data14 <- readRDS(file = "./DataFrames/df_source_all_00.rds") %>% 
    filter(., !(LINK_Twitter %in% NA))

# loading entire corpus & identifying missing ids
data15 <- readRDS(file = "./DataFrames/df_tweets_all.rds")
lst_help <- setdiff(x = data14$id, y = data15$id) # automatically

## substracting non-existent twitter ids
# defining manually checked ids
rm_id <- c(24, 42, 58, 60, 61, 74, 75, 84, 85, 102, 112, 123, 145, 541,
           571, 582, 590, 593, 705, 999, 1580, 1733, 1914, 2420, 3012,
           3585, 4523, 4597)

# elaborating remaining missing
lst_missed_06 <- setdiff(x = lst_help, y = rm_id)

# filtering source list for remaining
df_missed_06 <- data14 %>% 
  filter(., id %in% lst_missed_06) 

# removing terribly large files
rm(data14, data15)

# getting rid of language indicator for the second time (does not work with "get_timeline()")
df_missed_06$LINK_Twitter <- sub(pattern = "?lang=de", "", df_missed_06$LINK_Twitter, fixed = TRUE)
df_missed_06$LINK_Twitter <- sub(pattern = "?lang=fr", "", df_missed_06$LINK_Twitter, fixed = TRUE)
df_missed_06$LINK_Twitter <- sub(pattern = "?lang=en", "", df_missed_06$LINK_Twitter, fixed = TRUE)
df_missed_06$LINK_Twitter <- sub(pattern = "?lang=ar", "", df_missed_06$LINK_Twitter, fixed = TRUE)
df_missed_06$LINK_Twitter <- sub(pattern = "yvohofer/", "yvohofer", df_missed_06$LINK_Twitter, fixed = TRUE)
df_missed_06$LINK_Twitter <- sub(pattern = "rahel_estermann/", "rahel_estermann", df_missed_06$LINK_Twitter, fixed = TRUE)
df_missed_06$LINK_Twitter <- sub(pattern = "dominiccmueller/", "dominiccmueller", df_missed_06$LINK_Twitter, fixed = TRUE)
df_missed_06$LINK_Twitter <- sub(pattern = "nr_mayagraf", "mayagraf_bl", df_missed_06$LINK_Twitter, fixed = TRUE)

saveRDS(df_missed_06, file = "./DataFrames/df_missed_06.rds")

# creating support data frame
df_help0 <- rep(NA, 99) # creating support data frame

# actual scraping loop
for (i in 1:nrow(df_missed_06)) try({
  df_help <- df_missed_06[i, "LINK_Twitter"] %>% 
  sub(".*twitter.com/", "", .) %>% 
  get_timeline(., n = 3200)
  
  df_help$lastname <- df_missed_06[i, "lastname"]
  df_help$firstname <- df_missed_06[i, "firstname"]
  df_help$party_short <- df_missed_06[i, "party_short"]
  df_help$status <- df_missed_06[i, "status"]
  df_help$year_of_birth <- df_missed_06[i, "year_of_birth"]
  df_help$district <- df_missed_06[i, "district"] 
  df_help$zip <- df_missed_06[i, "zip"]
  df_help$gender <- df_missed_06[i, "gender"]
  df_help$nc <- df_missed_06[i, "nc"]
  df_help$sc <- df_missed_06[i, "sc"]
  df_help$incumbent <- df_missed_06[i, "incumbent"]
  df_help$id <- df_missed_06[i, "id"]
  
  df_help0 <- rbind(df_help0, df_help)
  
})

# saving missed
df_tweets_missed_06 <- df_help0
saveRDS(df_tweets_missed_06, file = "./DataFrames/df_tweets_missed_06.rds")

# binding to full data set and saving (full data set)
df_tweets_all <- readRDS("./DataFrames/df_tweets_all.rds")
df_tweets_all <- rbind(df_tweets_all, df_tweets_missed_06)
saveRDS(df_tweets_all, file = ("./DataFrames/df_tweets_all.rds"))

# removing auxillary variables
rm(i, df_help, df_help0, df_missed_06, df_tweets_all)


## Very last check
# manually scraping tweets
df_missed_07 <- (get_timeline("michelle__huber", n = 3200))

# getting the basic informaton of id 3669
df_basic_mh <- readRDS(file = "./DataFrames/df_source_all_00.rds") %>% 
  filter(., id %in% 3669) %>% 
  select(., lastname, firstname, party_short, year_of_birth, gender,
         district, zip, nc, sc, incumbent, id)

# loading the complete corpus
df_tweets_all <- readRDS("./DataFrames/df_tweets_all.rds")

# merging tweets, basic information and complete corpus
df_tweets_all <- cbind(df_missed_07, df_basic_mh) %>% 
  rbind(., df_tweets_all) %>% 
  arrange(., id)

# saving corpus
saveRDS(df_tweets_all, file = "./DataFrames/df_tweets_all.rds")

# removing auxillary variables
rm(df_basic_07, df_missed_07, df_tweets_all)

```